### 2017-04-18 paper/paper.tex
copy paper from crprolog

\documentclass{paper}

\begin{document}

\versions

Revising my paper before submitting for publication.

\bigskip

\begin{center}

{\Large \mytitle} \\ \medskip
\vp \\
\textit{\ttu}

\end{center}

\bigskip

\begin{abstract}

We study syntactic conditions which guarantee when
a \cplong{} program has antichain property
(no answer set is a proper subset of another).
A notable such condition is that
the program's dependency graph being acyclic
and having no directed path from one cr-rule head literal
to another.

\end{abstract}

\bigskip

\tableofcontents

\newpage

\begin{flushleft}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Introduction}

\aplong{} (\ap) is a programming language
for knowledge representation and reasoning.
Every \ap{} program has antichain property:
no answer set is a proper subset of another.
This property is desirable,
because we want minimal solutions
to planning and diagnostic problems.

\bigskip

\cplong{} (\cp) extends \ap{} with cr-rules.
In \cp, indirect exceptions can be elegantly encoded.
However, there exist \cp{} programs
without antichain property.
We investigate some syntactic conditions
guaranteeing that a \cp{} program
has this desired semantic property.
Such conditions are specified in Theorem \ref{last_theorem}
(most notable) as well as
Theorem \ref{antichain_a_prolog},
Corollary \ref{one_cr_rule},
and Propositions \ref{unique_cr_literals} \&
\ref{same_abductive_support_heads}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Preliminary Results}

\subsection{Background}

Note: the complete specifications of \ap{} and \cp{}
can be found in \cite[Sections 2.1, 2.2, 5.5]{krb}.
We focus on the \cp{} variant in which
minimality of abductive supports is based on cardinality.

\begin{definition}
[Regular Rule]

A \textdef{regular rule} has the form:
$$\regrule$$
where each $\lit_\ind$ is a ground literal and
$0 \le \nhl \le \nbl \le \nel$.

\end{definition}

\begin{definition}
[CR-Rule]

Similar to a regular rule,
a \textdef{cr-rule} has the form:
$$l_0 \whencr
l_1, \ldots, l_\nbl,\
not\ l_{\nbl + 1}, \ldots, not\ l_\nel.$$

\end{definition}

\begin{definition}
[\ap{} Program]

An \textdef{\ap{} program} is a finite set of
regular rules.

\end{definition}

\begin{definition}
[\cp{} Program]

A \textdef{\cp{} program} is a finite set of
regular rules and cr-rules.
Notations: $\preg$ and $\pcr$ denote
the corresponding subsets of regular rules and cr-rules.

\end{definition}

\begin{definition}
[Applications of CR-Rules]

Let $\rl$ be a cr-rule.
Then the \textdef{application} $\appl\rl$ is
the regular rule obtained from $\rl$ by
replacing $\whencr$ with $\when$.
If $\rls$ is a set of cr-rules, then let
$\appl\rls = \set{\appl\rl : \rl \in \rls}$.
When $\rls$ is a subset of a \cp{} program $\p$,
let $\pappld\rls$.

\end{definition}

\begin{definition}
[Antichain Property]

Let $\p$ be a \cp{} program.
We say $\p$ has \textdef{antichain property} if:
for all answer sets $\n\lits1$ and $\n\lits2$ of $\p$,
we have $\n\lits1 \sets \n\lits2 \impl \n\lits1 = \n\lits2$.

\end{definition}

\begin{example}
[\cp{} Program without Antichain Property]

Consider the following program:
\begin{gather*}
a. \\
\neg a \when \negd{b}, \negd{c}. \\
b \when c. \\
b \whencr. \tag{$\n\rl1$} \\
c \whencr. \tag{$\n\rl2$}
\end{gather*} \\
This program has answer sets $\n\lits1 = \{a, b\}$ and
$\n\lits2 = \{a, b, c\}$.
Observe that $\n\lits1 \setsp \n\lits2$ (proper subset).
The corresponding abductive supports are
$\n\rls1 = \set{\n\rl1}$ and $\n\rls2 = \set{\n\rl2}$.

\end{example}

\subsection{Up to One CR-Rule}

\begin{remark}
\label{vacuous_antichain}

Every inconsistent \cp{} program vacuously has
antichain property.
So only consistent programs are of interest.

\end{remark}

\begin{definition}
[Reduct]

Let $\rls$ be a set of regular rules and $\lits$ be a
consistent set of literals.
We write $\reduct{\rls}{\lits}$ for the \textdef{reduct} of
$\rls$ wrt $\lits$.

\end{definition}

\begin{lemma}
\label{reducts_subset}

Let $\p$ be an \ap{} program.
Let $\n\lits1$ and $\n\lits2$ be consistent sets of
literals.
If $\n\lits1 \sets \n\lits2$, then
$\reduct{\p}{\n\lits2} \sets \reduct{\p}{\n\lits1}$.

\end{lemma}

\begin{proof}

Assume $\reduct{\p}{\n\lits2}$ has an arbitrary rule $\rl$:
$$\regrulenodefneg$$
The corresponding rule in $\p$ is:
$$\regrule$$
For each $\ind$ in $\set{\nbl + 1, \ldots, \nel}$, we have
$l_\ind \notin \n\lits2$,
so $l_\ind \notin \n\lits1$ (as $\n\lits1 \sets \n\lits2$).
Therefore, $\rl$ is also a rule in $\reduct{\p}{\n\lits1}$.

\end{proof}

%:antichain A-Prolog
\begin{theorem}
[Antichain Property of \ap{} Programs, proved by \mg]
\label{antichain_a_prolog}

Let $\p$ be an \ap{} program.
Let $\n\lits1 \sets \n\lits2$ be answer sets of $\p$.
Then $\n\lits1 = \n\lits2$.

\end{theorem}

\begin{proof}

We will show $\n\lits2 \sets \n\lits1$.

\begin{enumerate}
\item
First, $\n\lits2$ is an answer set of
$\reduct{\p}{\n\lits2}$.
So $\n\lits2$ is a minimal (wrt set inclusion)
consistent set of literals which
satisfies $\reduct{\p}{\n\lits2}$.
We shall prove $\n\lits2 \sets \n\lits1$ by showing
$\n\lits1$ also satisfies $\reduct{\p}{\n\lits2}$.
\item
By \ref{reducts_subset}, we have $\reduct{\p}{\n\lits2}
\sets\reduct{\p}{\n\lits1}$.
Because $\n\lits1$ satisfies $\reduct{\p}{\n\lits1}$,
we know $\n\lits1$ also satisfies $\reduct{\p}{\n\lits2}$.
\end{enumerate}

\end{proof}

\begin{definition}
[Equivalence of \cp{} Programs]

Let $\n\p1$ and $\n\p2$ be \cp{} programs.
We say $\n\p1$ and $\n\p2$ are \textdef{equivalent},
denoted by $\n\p1 \equi \n\p2$, when
$\lits$ is an answer set of $\n\p1$ iff $\lits$ is an
answer set of $\n\p2$ for every consistent set of literals
$\lits$.
\end{definition}

\begin{remark}
\label{consistent_p_reg}

Let $\p$ be a \cp{} program.
If $\preg$ is consistent, then $\p$ is equivalent to
$\preg$, which has antichain property due to Theorem
\ref{antichain_a_prolog}.
The interesting case is when $\preg$ is inconsistent.

\end{remark}

\begin{corollary}
\label{one_cr_rule}

Let $\p$ be a \cp{} program where \inconspreg{}.
If $\p$ has only one cr-rule, then $\p$ has
antichain property.

\end{corollary}

\begin{proof}

Assume $\pcr = \set\rl$ for some cr-rule $\rl$.
Then $\p$ is equivalent to the \ap{} program
$\pappld{\set\rl}$.
Simply apply Theorem \ref{antichain_a_prolog} to
$\pappl{\set\rl}$.

\end{proof}

\subsection{Unique CR-Literals}

\begin{definition}
[Useless Regular Rule]

Let $\p$ be an \ap{} program containing some rule $\rl$.
For an answer set $\lits$ of $\p$, we say $\rl$ is
\textdef{useless} wrt $\lits$ if $\lits$ is an answer set
of $\p \setd \set\rl$.

\end{definition}

\begin{definition}
[Regular Rule Firing]

Given a regular rule $\rl$ and a consistent set of literals
$\lits$, we say $\rl$ \textdef{fires} wrt $\lits$ if
$\lits$ satisfies the body of $\rl$.

\end{definition}

\begin{lemma}
\label{unreduced_rule_fires_iff}

Let $\rl$ be a regular rule and $\lits$ be a
consistent set of literals.
Assume $\reduct{\set\rl}\lits = \set{\ot\rl}$ for some
\dnf{} rule $\ot\rl$.
Then $\rl$ fires iff $\ot\rl$ fires, wrt $\lits$.

\end{lemma}

\begin{proof}

The two rules are:
\begin{gather*}
\regrule \tag{$\rl$} \\
\regrulenodefneg \tag{$\ot\rl$}
\end{gather*} \\
By construction of $\ot\rl$ from $\rl$,
we know $\n\lit\ind \not\in \lits$ for all $\ind \in
\set{\nbl + 1, \ldots, \nel}$.
Then $\rl$ fires wrt $\lits$ iff
$\n\lit\ind \in \lits$ for all
$\ind \in \set{\nhl + 1, \ldots, \nbl}$ iff
$\ot\rl$ fires wrt $\lits$.

\end{proof}

\begin{remark}
\label{superset_fires}

Let $\rl$ be a regular \dnf{} rule and
$\n\lits1 \sets \n\lits2$ be consistent sets of literals.
If $\rl$ fires wrt $\n\lits1$, then $\rl$ fires wrt
$\n\lits2$.

\end{remark}

\begin{lemma}
\label{useless_unless_fires}

Let $\p$ be an \ap{} program containing some rule $\rl$.
Let $\lits$ be an answer set of $\p$.
If $\rl$ does not fire, then $\rl$ is useless, wrt $\lits$.

\end{lemma}

\begin{proof}

Let $\n\p1 = \reduct\p\lits$ and
$\n\p2 = \reduct{(\p \setd \set\rl)}\lits$.
We know $\lits$ is an answer set of $\n\p1$.
We will prove $\lits$ is an answer set of $\n\p2$.

\begin{enumerate}

\item
First, $\lits$ satisfies $\n\p1$. Notice
$\n\p2 \sets \n\p1$.
Then $\lits$ satisfies $\n\p2$.

\item
Assume some consistent set of literals
$\ot\lits \sets \lits$ also satisfies $\n\p2$.
We shall show $\ot\lits = \lits$.
\begin{enumerate}
\item
Case 1 of 2: $\reduct{\set\rl}\lits = \sete$.
Then $\n\p1 = \n\p2$, so $\ot\lits$ satisfies $\n\p1$.
\item
Case 2 of 2: $\reduct{\set\rl}\lits = \set{\ot\rl}$ for
some \dnf{} rule $\ot\rl$.
Recall that we hypothesized $\rl$ does not fire wrt
$\lits$. By Lemma \ref{unreduced_rule_fires_iff}, we know
$\ot\rl$ does not fire wrt $\lits$.
Since $\ot\lits \sets \lits$, using the contrapositive of
Remark \ref{superset_fires},
we deduce that $\ot\rl$ does not fire wrt $\ot\lits$.
Then $\ot\lits$ vacuously satisfies $\ot\rl$.
So $\ot\lits$ satisfies $\n\p1 = \n\p2 \setu \set{\ot\rl}$.
\end{enumerate}
In both cases, $\ot\lits$ satisfies $\n\p1$.
As $\lits$ is an answer set of $\n\p1$, due to minimality,
we know $\lits \sets \ot\lits$.
Since we assumed $\ot\lits \sets \lits$, we can now
conclude that $\ot\lits = \lits$.

\item
We have shown that $\lits$ is a minimal consistent set of
literals which satisfies $\n\p2$.
Hence, $\lits$ is an answer set of $\n\p2$.

\end{enumerate}

\end{proof}

\begin{lemma}
\label{cr_rule_not_useless}

Let $\p$ be a \cp{} program.
Let $\lits$ be an answer set of $\p$ and $\rls$ be a
corresponding abductive support.
Let cr-rule $\rl \in \rls$.
Then $\appl\rl$ is not useless wrt $\lits$.

\end{lemma}

\begin{proof}

By way of contradiction, assume $\appl\rl$ is useless wrt
$\lits$.
Let $\pappld\rls$.
Then $\lits$ is an answer set of
$\pappl\rls \setd \set{\appl\rl}$,
whereas this program is precisely $\pappld{\ot\rls}$ with
$\ot\rls = \rls \setd \set\rl$.
So $\pappl{\ot\rls}$ is consistent.
Since $\rls$ is a minimal (wrt cardinality) set of cr-rules
whose applications make $\p$ consistent,
we have $|\rls| \le |\ot\rls|$.
However, $|\ot\rls| = |\rls| - 1$
(recall $\ot\rls = \rls \setd \set\rl$), contradiction.

\end{proof}

\begin{lemma}
\label{abductive_support_fires}

Let $\p$ be a \cp{} program.
Let $\lits$ be an answer set of $\p$ and $\rls$ be a
corresponding abductive support.
Let cr-rule $\rl \in \rls$.
Then the application $\appl\rl$ fires wrt $\lits$.

\end{lemma}

\begin{proof}

First, $\lits$ is an answer set of $\pappld\rls$.
By way of contradiction, assume there exists some cr-rule
$\rl \in \rls$ such that
$\appl\rl$ does not fire wrt $\lits$.
By Lemma \ref{useless_unless_fires}, $\appl\rl$ is useless
wrt $\lits$.
However, by \ref{cr_rule_not_useless}, $\appl\rl$ is not
useless wrt $\lits$, contradiction.

\end{proof}

\begin{definition}
[Head]

If $\rl$ is a rule, then let $\head\rl$ denotes the set of
literals which appear in the head of $\rl$.
If $\rls$ is a set of rules, then let
$\head\rls = \bigcup_{\rl \in \rls} \head\rl$.

\end{definition}

%:supported literal
\begin{definition}
[Supported Literal]

Let $\rl$ be a regular rule,
$\lit$ be a literal,
and $\lits$ be a consistent set of literals.
We say $\lit$ is \textdef{supported} by $\rl$ wrt $\lits$
if all of the following hold:
\begin{enumerate}
\item
$\rl$ fires wrt $\lits$
\item
$\head\rl \seti \lits = \set\lit$
\end{enumerate}
\cite[page 43, Proposition 2.2.1]{krb}

\end{definition}

\begin{proposition}
\label{unique_cr_literals}

Let $\p$ be a \cp{} program.
If the literal in the head of each cr-rule does not appear
in the head of any other rule,
then $\p$ has antichain property.

\end{proposition}

\begin{proof}

Let $\n\lits1$ and $\n\lits2$ be answer sets of $\p$.
Assume $\n\lits1 \sets \n\lits2$.
We will show $\n\lits1 = \n\lits2$.

\begin{enumerate}

\item
Let $\n\rls1$ and $\n\rls2$ respectively be abductive
supports for $\n\lits1$ and $\n\lits2$.
We first prove $\n\rls1 \sets \n\rls2$.
Let $\rl$ be an arbitrary cr-rule in $\n\rls1$.
By Lemma \ref{abductive_support_fires},
$\rl$ fires wrt $\n\lits1$, and
$\n\lits1$ satisfies $\head\rl = \set{\lit}$
where $\lit$ is a literal.
So $\lit \in \n\lits1$, then $\lit \in \n\lits2$
(as $\n\lits1 \sets \n\lits2$).
By the hypothesized syntactic condition, $\rl$ is the sole
rule in $\p$ whose head contains $\lit$.
Then only $\rl$ can support $\lit$ wrt $\n\lits2$.
So $\rl \in \n\rls2$.

\item
Now that we showed $\n\rls1 \sets \n\rls2$,
recall $|\n\rls1| = |\n\rls2|$,
as both are abductive supports.
Then $\n\rls1 = \n\rls2$, since they are finite sets.
Consequently, $\pappld{\n\rls1}$ equals $\pappld{\n\rls2}$.
So $\n\lits1$ and $\n\lits2$ are answer sets of the same
\ap{} program.
By Theorem \ref{antichain_a_prolog}, $\n\lits1 = \n\lits2$.

\end{enumerate}

\end{proof}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Main Results}

\subsection{Dependency Graphs}

\begin{definition}
[Positive Body of Rule]

Let $\rl$ be a rule.
The \textdef{positive body} of $\rl$,
denoted by $\posbody\rl$,
is the set of literals in the body of $\rl$ which are
\dnf.

\end{definition}

\begin{definition}
[Dependency Graph]

Let $\p$ be a \cp{} program.
Let $\g\p$ be a graph whose vertices are literals of $\p$.
For each pair of vertices $\n\lit1$ and $\n\lit2$ of
$\g\p$, there is a directed edge to $\n\lit1$ from
$\n\lit2$ if $\p$ has some rule $\rl$ where
$\n\lit1 \in \head\rl$ and $\n\lit2 \in \posbody\rl$.
We say $\g\p$ is the \textdef{dependency graph} of $\p$.
Note: a self-loop forms a directed cycle.

\end{definition}

\begin{remark}
[Answer Set of Acyclic Program]
\label{acyclic_answer_set}

Let $\p$ be an acyclic \ap{} program and $\lits$ be a
consistent set of literals.
Then $\lits$ is an answer set of $\p$ iff every literal in
$\lits$ is supported by a rule in $\p$ wrt $\lits$
\cite[page 58, Theorem 2.7]{hcfb}.

\end{remark}

%:ex self-loop
\begin{example}
[Self-Loop Forming Cycle]

To the contrary, assume a self-loop does not form a cycle.
Consider this \ap{} program:
\begin{gather*}
\lit \when \lit. \tag{$\rl$}
\end{gather*}
Let $\lits = \set{\lit}$.
Notice that $\lit$ is supported by $\rl$ wrt $\lits$.
However, $\lits$ is not an answer set of $\p$.
Then Remark \ref{acyclic_answer_set} is wrong,
contradiction.

\end{example}

\begin{definition}
[Head-Cycle]

Let $\p$ be a \cp{} program with dependency graph $\g\p$.
Let $\cy$ be a cycle in $\g\p$.
Assume:
\begin{enumerate}
\item
vertices $\n\lit1$ and $\n\lit2$ are in $\cy$
\item
there exists $\rl \in \p$ where
$\n\lit1$ and $\n\lit2$ are in $\head\rl$
\end{enumerate}
Then $\cy$ is called a \textdef{\hc} in $\p$.

\end{definition}

\begin{definition}
[Dependent Literals]

Let $\p$ be a \cp{} program with dependency graph $\g\p$.
Let $\n\lit1$ and $\n\lit2$ be two literals appearing in
$\p$.
We say $\n\lit1$ \textdef{depends} on $\n\lit2$ if
$\g\p$ has a directed path to $\n\lit1$ from $\n\lit2$.

\end{definition}

\begin{definition}
[CR-Literal]

Let $\p$ be \cp{} program with cr-rule $\rl$ where
$\head\rl = \set\lit$.
We say $\lit$ is a \textdef{cr-literal} of $\p$.

\end{definition}

\begin{definition}
[CR-Independence]

Let $\p$ be a \cp{} program.
Then $\p$ is \textdef{cr-independent} if
$\n\lit1$ does not depend on $\n\lit2$
for all cr-literals $\n\lit1$ and $\n\lit2$.

\end{definition}

\subsection{Same Abductive Support Heads}

\begin{remark}

Let $\p$ be a \cp{} program with some answer set $\lits$.
Then $\lits \sets \head\p$.

\end{remark}

\begin{remark}
\label{empty_reduct_unless_fires}

Let $\rl$ be a regular rule and $\lits$ be a consistent set
of literals.
If $\rl$ fires wrt $\lits$, then
$\reduct{\set\rl}\lits \ne \sete$.

\end{remark}

\begin{remark}
\label{nonempty_reduced_cr_rule}

Let $\p$ be a \cp{} program with some answer set $\lits$
and a corresponding abductive support $\rls$.
Let cr-rule $\rl \in \rls$. Then
$\reduct{\set{\appl\rl}}\lits \ne \sete$.
(Use Lemma \ref{abductive_support_fires} and Remark
\ref{empty_reduct_unless_fires}.)

\end{remark}

\begin{example}

Consider an inconsistent \ap{} program $\p$:
$$\lit \when \negd\lit.$$
Let $\lits = \set\lit$.
Notice $\lits$ is a minimal consistent set of literals
which satisfies $\p$.
However, $\lits$ is not an answer set of $\p$, because
$\lits$ nonminimally satisfies $\reduct\p\lits = \sete$.
(Note that $\ot\lits = \sete$ satisfies neither $\p$ nor
$\reduct\p{\ot\lits} = \set{\lit.}$.)

\end{example}

\begin{example}

Consider a consistent \cp{} program $\p$:
\begin{gather*}
\when \negd {\n\lit1}, \negd {\n\lit2}. \\
\n\lit1 \whencr \negd {\n\lit2}. \tag{$\rl$}
\end{gather*} \\
Then $\rls = \set\rl$ is an abductive support of $\p$.
Indeed, let $\pappld\rls$,
then $\lits = \set{\n\lit1}$ is an answer set of
$\reduct{\pappl\rls}\lits = \set{\n\lit1}$.
Notice $\ot\lits = \set{\n\lit2}$ satisfies $\pappl\rls$,
but $\n\lit1 \not\in \ot\lits$.

\end{example}

\begin{lemma}
\label{intersection_satisfies}

Let $\p$ be a nondisjunctive \dnf{} \ap{} program.
If consistent sets of literals $\n\lits1$ and $\n\lits2$
satisfy $\p$,
then $\n\lits0 = \n\lits1 \seti \n\lits2$ also satisfies
$\p$.

\end{lemma}

\begin{proof}

Let $\rl$ be a rule in $\p$.
Assume $\rl$ fires wrt $\n\lits0$.
Then $\rl$ also fires wrt $\n\lits1$ and $\n\lits2$
(as $\p$ is \dnf).
So $\n\lits1$ and $\n\lits2$ satisfy $\head\rl = \set\lit$
(since $\p$ is nondisjunctive).
Thus $\lit$ is in $\n\lits1$, $\n\lits2$, and $\n\lits0$.

\end{proof}

\begin{lemma}
[Proved by \mg]
\label{answer_set_subprogram}

Let $\p$ be a nondisjunctive \dnf{} \ap{} program.
Assume $\p$ has rules $\n\rl1 \ne \n\rl2$ such that
$\head{\n\rl1} = \head{\n\rl2}$.
Let $\n\p0 = \p \setd \set{\n\rl1, \n\rl2}$,
$\n\p1 = \n\p0 \setu \set{\n\rl1}$,
and $\n\p2 = \n\p0 \setu \set{\n\rl2}$.
If $\lits$ is an answer set of $\p$, then $\lits$ is also
an answer set of either $\n\p1$ or $\n\p2$.

\end{lemma}

\begin{proof}

To the contrary, assume $\lits$ is an answer set of neither
$\n\p1$ nor $\n\p2$.
Still, $\lits$ satisfies both $\n\p1$ and $\n\p2$
(as $\lits$ satisfies $\p$).
So there exist two proper subsets of $\lits$, say
$\n\lits1$ and $\n\lits2$,
which respectively satisfy $\n\p1$ and $\n\p2$
(the programs are \dnf{}).

\begin{enumerate}

\item
Case 1 of 2: either $\n\rl1$ fires wrt $\n\lits1$, or
$\n\rl2$ fires wrt $\n\lits2$.
WOLOG, assume the former. Then $\n\lits1$ satisfies
$\head{\n\rl1} = \head{\n\rl2}$.
So $\n\lits1$ also satisfies both the rule $\n\rl2$ and the
program $\p = \n\p1 \setu \set{\n\rl2}$.
Recall that $\lits$ is an answer set of $\p$ whereas
$\n\lits1 \setsp \lits$, contradiction.

\item
Case 2 of 2: neither $\n\rl1$ fires wrt $\n\lits1$, nor
$\n\rl2$ fires wrt $\n\lits2$.
So neither $\n\rl1$ nor $\n\rl2$ fires wrt
$\n\lits0 = \n\lits1 \seti \n\lits2$
(the rules are \dnf).
Then $\n\lits0$ vacuously satisfies $\n\rl1$ and $\n\rl2$.
Because $\n\lits1$ and $\n\lits2$ satisfy $\n\p0$,
by \ref{intersection_satisfies},
$\n\lits0$ satisfies $\n\p0$ too.
Therefore, $\n\lits0$ satisfies
$\p = \n\p0 \setu \set{\n\rl1, \n\rl2}$.
But $\lits$ is an answer set of $\p$, and
$\n\lits0 \setsp \lits$, contradiction.

\end{enumerate}

\end{proof}

%:diff cr-literals
\begin{lemma}
\label{diff_cr_literals}

Let $\p$ be a nondisjunctive \cp{} program with some
abductive support $\rls$.
Then for all cr-rules $\n\rl1$ and $\n\rl2$ in $\rls$,
we have
$\head{\n\rl1} = \head{\n\rl2} \impl \n\rl1 = \n\rl2$.

\end{lemma}

\begin{proof}

By way of contradiction, assume there exist cr-rules
$\n\rl1\ne \n\rl2$ in $\rls$ where
$\head{\n\rl1} = \head{\n\rl2}$.
Some notations:
\begin{enumerate}
\item
Let $\n\rls1 = \rls \setd \set{\n\rl2}$ and
$\n\rls2 = \rls \setd \set{\n\rl1}$.
\item
Let $\n\p1 = \applp{\n\rls1}$ and
$\n\p2 = \applp{\n\rls2}$.
\item
Let $\lits$ be an answer set of $\p$ wrt $\rls$.
\item
Let $\n\p a = \reduct{\n\p1}\lits$ and
$\n\p b = \reduct{\n\p2}\lits$.
Note that by \ref{nonempty_reduced_cr_rule},
$\reduct{\set{\appl{\n\rl1}}}\lits = \set{\ot{\n\rl1}}$ and
$\reduct{\set{\appl{\n\rl2}}}\lits = \set{\ot{\n\rl2}}$ for
some \dnf{} rules $\ot{\n\rl1}$ and $\ot{\n\rl2}$.
\end{enumerate}

By \ref{answer_set_subprogram}, $\lits$ is an answer set of
either $\n\p a$ or $\n\p b$.
WOLOG, assume the former.
Then $\lits$ is an answer set of $\n\p1$.
So $\n\rls1$ is an abductive support of $\p$,
but $|\n\rls1| < |\rls|$, contradiction.

\end{proof}

%:sole supporting rule
\begin{lemma}
\label{sole_supporting_rule}

Let $\p$ be an acyclic \cp{} program having some answer set
$\lits$ wrt an abductive support $\rls$.
Let cr-rule $\rl \in \rls$ where $\head\rl = \set\lit$.
Then $\appl\rl$ is the only rule in $\pappld\rls$ which
supports $\lit$ wrt $\lits$.

\end{lemma}

\begin{proof}

By way of contradiction, assume $\lit$ is also supported by
a rule $\ot\rl \ne \appl\rl$ in $\pappl\rls$.
Let $\ot\rls = \rls \setd \set{\rl}$ and
$\ot\p = \applp{\ot\rls}$.
We will prove $\lits$ is an answer set of $\ot\p$:
\begin{enumerate}
\item
First, $\lits$ satisfies $\ot\p \sets \pappl\rls$.
\item
Let $\ot\lit$ be an arbitrary literal in $\lits$. We show
$\ot\lit$ is supported wrt $\lits$ by some rule in $\ot\p$.
Recall that $\lits$ is an answer set of $\pappl\rls$.
By \ref{acyclic_answer_set}, $\ot\lit$ is supported wrt
$\lits$ by some rule $\n\rl0$ in $\pappl\rls$.
\begin{enumerate}
\item
Case 1 of 2: $\n\rl0 = \appl\rl$.
Recall $\head\rl = \set\lit$.
Then $\ot\lit = \lit$.
Notice $\ot\rl$ also supports $\ot\lit$ wrt $\lits$, and
$\ot\rl \in \ot\p$.
\item
Case 2 of 2: $\n\rl0 \ne \appl\rl$.
Then $\n\rl0 \in \ot\p$.
\end{enumerate}
\end{enumerate}
So $\ot\p$ is consistent, and $\ot\rls$ is an abductive
support of $\p$.
But $|\ot\rls| < |\rls|$, contradiction.

\end{proof}

\begin{definition}
[Factified Rule]

Let $\rl$ be a regular rule.
Let $\factify\rl$ denote the \textdef{factified rule}
obtained from $\rl$ by dropping its body.
If $\rls$ is a set of rules, then let
$\factify\rls = \set{\factify\rl : \rl \in \rls}$.

\end{definition}

%:factify answer set
\begin{lemma}
\label{factify_answer_set}

Let $\p$ be a \cp{} program with answer set $\lits$ and
corresponding abductive support $\rls$.
Then $\lits$ is an answer set of
$\ot\p = \preg \setu \factify{\appl\rls}$.

\end{lemma}

\begin{proof}
We prove $\lits$ is a minimal consistent set of literals
which satisfies $\reduct{\ot\p}\lits$:
\begin{enumerate}
\item
Let $\pappld\rls$.
Note that $\head\rls \sets \lits$ as $\lits$ is an answer
set of $\pappl\rls$.
Then $\lits$ satisfies
$\reduct{\ot\p}\lits =
\reduct{(\preg)}{\lits} \setu \factify{\appl\rls}$.
\item
Assume some $\ot\lits \sets \lits$ also satisfies
$\reduct{\ot\p}\lits$.
We know $\head\rls \sets \ot\lits$.
Then $\ot\lits$ satisfies
$\reduct{(\pappl\rls)}\lits =
\reduct{(\preg)}\lits \setu \reduct{(\appl\rls)}\lits$.
So $\lits \sets \ot\lits$
(as $\lits$ is an answer set of
$\pappl\rls$). Therefore $\ot\lits = \lits$.
\end{enumerate}

\end{proof}

%:same abductive support heads
\begin{proposition}
\label{same_abductive_support_heads}

Let $\p$ be a \cp{} program.
Then $\p$ has antichain property if
$\head{\n\rls1} = \head{\n\rls2}$ for
all abductive supports $\n\rls1$ and $\n\rls2$ of $\p$.

\end{proposition}

\begin{proof}

Let $\n\lits1$ and $\n\lits2$ be arbitrary answer sets of
$\p$ corresponding to
some abductive supports $\n\rls1$ and $\n\rls2$.
By \ref{factify_answer_set}, $\n\lits1$ and $\n\lits2$ are
respectively answer sets of
$\preg \setu \factify{\appl{\n\rls1}}$ and
$\preg \setu \factify{\appl{\n\rls2}}$,
which are the same \ap{} program because
$\head{\n\rls1} = \head{\n\rls2}$.
By Theorem \ref{antichain_a_prolog},
$\n\lits1 \sets \n\lits2 \impl \n\lits1 = \n\lits2$.

\end{proof}

\subsection{CR-Independence and Acyclicity}

%:proof of literal
\begin{definition}
[Proof of Literal]

Let $\p$ be an \ap{} program,
$\lits$ be a consistent set of literals,
and $\lit$ be a literal.
A \textdef{proof} of $\lit$ wrt $\lits$ in $\p$ is
a nonempty sequence of rules
$\pr = \n\rl1, \ldots, \n\rl n$ in $\p$ such that:
\begin{enumerate}
\item
for each rule $\n\rl i$, there is a (sole) literal
$\ot\lit$ supported by $\rl$ wrt $\lits$;
let $h_\lits(\rl)$ denote $\ot\lit$
\item
$\lit = h_\lits(\n\rl n)$
\item
$\posbody{\n\rl1} = \sete$
%:hcf error
\footnote
{Their original definition states: $\n\rl1$ is a fact.
However, there is an error in their Lemma B.5 on page 83.
Consider an acyclic \ap{} program $\set{a \when \negd b.}$
with answer set $\set{a}$.}
\item
for each rule $\n\rl i$,
every literal in $\posbody{\n\rl i}$ is $h_\lits(\n\rl j)$
for some $j < i$
\end{enumerate}
\cite[page 57]{hcfb}

\end{definition}

\begin{definition}

Additional notations:
\begin{enumerate}
\item
$\prs{\lit}{\lits}{\p}$ denotes the set of all proofs $\pr$
of $\lit$ wrt $\lits$ in $\p$
\item
$h_\lits(\pr)$ denotes $\set{h_\lits(\rl) : \rl \in \pr}$
\item
$\posbody\pr$ denotes $\set{\posbody\rl : \rl \in \pr}$
\end{enumerate}

\end{definition}

\begin{remark}

Let $\pr = \rlseq1n \in \prs\lit\lits\p$.
We adopt the convention that the rules in $\pr$ are
pairwise distinct.
Indeed, if there were $\n\rl i = \n\rl j$ where
$i < j$, then $\ot\pr =
\rlseq1{j - 1}, \rlseq{j + 1}n \in \prs\lit\lits\p$,
so $\n \rl j$ would be redundant.

\end{remark}

\begin{remark}

Let $\p$ be a \hcf{} \ap{} program with answer set $\lits$.
Then each literal in $\lits$ has a proof wrt $\lits$ in
$\p$ \cite[page 57]{hcfb}.

\end{remark}

\begin{definition}
[Rank of Literal]

Let $\p$ be a \hcf{} \ap{} program and
$\lits$ be a consistent set of literals.
The \textdef{rank} of a literal $\lit$ wrt $\lits$ in $\p$,
denoted by $\rkt\lit\lits\p$, is
$min\set{|\pr| : \pr \in \prs\lit\lits\p}$.

\end{definition}

\begin{definition}
[Ranking Function]

Let:
\begin{enumerate}
\item
$\p$ be a \hcf{} \ap{} program
\item
$\lits$ be an answer set of $\p$
\item
function $\rkn : \lits \to \mathbb{N}$
\end{enumerate}

Then $\rkn$ is the \textdef{ranking function}
wrt $\lits$ in $\p$ if $\rku\lit = \rkt\lit\lits\p$
for all $\lit \in \lits$.

\end{definition}

\begin{definition}
[Normal Proof of Literal]

Let:
\begin{enumerate}
\item
$\p$ be a \hcf{} \ap{} program
\item
$\lits$ be an answer set of $\p$
\item
$\lit \in \lits$
\item
$\pr \in \prs\lit\lits\p$
\item
$\rkn$ be the ranking function wrt $\lits$ in $\p$
\end{enumerate}

We say $\pr$ is a \textdef{normal proof} if
for all $\rl \in \pr$ and $\ot\lit \in \posbody\rl$,
we have $\rku{\ot\lit} < \rku{h_\lits(\rl)}$.

\end{definition}

\begin{remark}

Let:
\begin{enumerate}
\item
$\p$ be a \hcf{} \ap{} program
\item
$\lits$ be an answer set of $\p$
\item
$\rkn$ be the ranking function wrt $\lits$ in $\p$
\item
$\lit \in \lits$
\item
normal $\pr = \rlseq1n \in \prs\lit\lits\p$
\item
$\n\rl i \in \pr$
\item
$\n\lit i \in \posbody{\n\rl i}$.
\end{enumerate}

Then:
\begin{enumerate}
\item
$\rku{\n\lit i} < \rku\lit$
\item
$\rlseq1i$ is a normal proof of $h_\lits(\n\rl i)$
\end{enumerate}

\end{remark}

%:ex nonminimal subproof
\begin{example}
[Nonminimal Subproof of Minimal Proof]

Consider this acylic \ap{} program $\p$:
\begin{gather}
a \when b, c. \\
b \when c1x. \\
c \when c1x. \\
c1x \when c1y. \\
c1y. \\
c \when c2. \\
c2.
\end{gather} \\
The sole answer set of $\p$ is
$\lits = \set{a, b, c, c1x, c1y, c2}$.
The only minimal proofs of literal $a$ wrt
$\lits$ in $\p$ are
the two sequences of rules $<5, 4, 3, 2, 1>$ and
$<5, 4, 2, 3, 1>$.
In both these proofs, the subproof of $c$ is $<5, 4, 3>$,
which is nonminimal.
(The minimal proof of $c$ wrt $\lits$ in $\p$ is $<7, 6>$.)

\end{example}

%:rule in P2
\begin{lemma}
\label{rule_in_P2}

Let:
\begin{enumerate}
\item
$\n\p1$ and $\n\p2$ be \hcf{} \ap{} programs with
corresponding answer sets $\n\lits1 \setsp \n\lits2$
\item
$\lit \in \n\lits2 \setd \n\lits1$
\end{enumerate}

Then for each normal
$\pr = \rlseq1n \in \prs\lit{\n\lits2}{\n\p2}$,
there exists $\rl \in \pr$ such that
$\rl \in \n\p2 \setd \n\p1$.

\end{lemma}

\begin{proof}

Let $\rkn$ be the ranking function
wrt $\n\lits2$ in $\n\p2$.
We employ induction on $\rku\lit$.

\begin{enumerate}

\item
Base step: $\rku\lit = min\set{\rku{\ot\lit} :
\ot\lit \in \n\lits2 \setd \n\lits1}$.
\begin{enumerate}
\item
To the contrary, assume for every $\rl \in \pr$, we have
$\rl \in \n\p1 \seti \n\p2$.
\item
Then $\n\rl n \in \n\p1$.
\item
As $\pr$ is normal, for each
$\ot\lit \in \posbody{\n\rl n}$,
we have $\rku{\ot\lit} < \rku\lit$,
so $\ot\lit \in \n\lits1$.
\item
Then $\n\rl n$ fires wrt $\n\lits1$.
\item
As $\n\lits1$ is an answer set of $\n\p1$, we know
$\n\lits1$ satisfies $\head{\n\rl n}$.
\item
Let $\ot\lit \in \head{\n\rl n}$.
\begin{enumerate}
\item
Case 1 of 2: $\ot\lit = \lit$.
We already assumed $\lit \in \n\lits2 \setd \n\lits1$.
\item
Case 2 of 2: $\ot\lit \ne \lit$.
We have $\ot\lit \not\in \n\lits2$,
so $\ot\lit \not\in \n\lits1$.
\end{enumerate}
\item
So $\n\lits1$ does not satisfy $\head{\n\rl n}$,
contradiction.
\end{enumerate}
\item
Induction step: $\rku\lit \le max\set{\rku{\ot\lit} :
\ot\lit \in \n\lits2 \setd \n\lits1}$.
\begin{enumerate}
\item
Induction hypothesis: for each
$\ot\lit \in \n\lits2 \setd \n\lits1$,
let normal $\ot\pr \in \prs{\ot\lit}{\n\lits2}{\n\p2}$,
if $\rku{\ot\lit} < \rku\lit$,
then there exists ${\rl} \in \ot\pr$
such that ${\rl} \in \n\p2 \setd \n\p1$.
\item
To the contrary, assume for every $\rl \in \pr$, we have
$\rl \in \n\p1 \seti \n\p2$.
\begin{enumerate}
\item
Case 1 of 2: there exists $\ot\lit \in \posbody{\n\rl n}$
where $\ot\lit \in \n\lits2 \setd \n\lits1$.
\begin{enumerate}
\item
Choose some $1 \le m \le n$ where
$h_{\n\lits2}(\n\rl m) = \ot\lit$.
\item
As $\pr$ is normal, $\ot\pr = \n\rl1, \ldots, \n\rl m$ is a
normal proof of
$\ot\lit$ wrt $\n\lits2$ in $\n\p2$.
\item
Notice $\rku{\ot\lit} < \rku\lit$.
\item
By the induction hypothesis, $\ot\pr$ contains some
${\rl} \in \n\p2 \setd \n\p1$.
\item
So $\pr$ also contains ${\rl}$.
\item
By our assumption, $\rl \in \n\p1 \seti \n\p2$,
contradiction.
\end{enumerate}
\item
Case 2 of 2: for every $\ot\lit \in \posbody{\n\rl n}$,
we have $\ot\lit \in \n\lits1$.
\begin{enumerate}
\item
Then $\n\rl n$ fires wrt $\n\lits1$.
\item
By our assumption, $\n\rl n \in \n\p1$.
\item
As $\n\lits1$ is an answer set of $\n\p1$, we know
$\n\lits1$ satisfies $\head{\n\rl n}$.
\item
But $\head{\n\rl n} \seti \n\lits1 = \sete$, contradiction.
\end{enumerate}
\end{enumerate}
\end{enumerate}

\end{enumerate}

\end{proof}

\begin{remark}

Let $\pr = \n\rl1, \ldots, \n\rl n \in \prs\lit\lits\p$. If
$\pr$ is minimal, then:
\begin{enumerate}
\item
$\pr$ is normal
\item
$\lit$ depends on $h_\lits(\n\rl i)$ for all $i < n$
\end{enumerate}

\end{remark}

%:last lemma
\begin{lemma}
\label{last_lemma}

Let $\p$ be a nondisjunctive acyclic \cp{} program.
If $\p$ has answer sets $\n\lits1 \setsp \n\lits2$,
then there exist literals $\n\lit1$ and $\n\lit2$ in
$\head\pcr$ such that
$\n\lit1$ depends on $\n\lit2$.

\end{lemma}

\begin{proof}

Notations:
\begin{enumerate}
\item
By the contrapositive of Proposition \ref{same_abductive_support_heads},
there exist abductive supports
$\n\rls1$ and $\n\rls2$ of $\p$ where
$\head{\n\rls1} \ne \head{\n\rls2}$.
\item
Let $\ot{\n\rls1} = \factify{\appl{\n\rls1}}$ and
$\ot{\n\rls2} = \factify{\appl{\n\rls2}}$.
\item
Let $\n\p1 = \preg \setu \ot{\n\rls1}$ and
$\n\p2 = \preg \setu \ot{\n\rls2}$.
By Lemma \ref{factify_answer_set},
$\n\lits1$ and $\n\lits2$ are respectively answer sets of
$\n\p1$ and $\n\p2$.
\end{enumerate}

We follow these steps:
\begin{enumerate}
\item
By Lemma \ref{diff_cr_literals},
since $\p$ is nondisjunctive, we have
$|\ot{\n\rls1}| = |\n\rls1|$ and
$|\ot{\n\rls2}| = |\n\rls2|$.
\item
Notice $|\n\rls1| = |\n\rls2| > 0$.
\item
Then $|\ot{\n\rls1}| = |\ot{\n\rls2}| > 0$.
\item
Observe $|\head{\ot{\n\rls1}}| = |\ot{\n\rls1}|$ and
$|\head{\ot{\n\rls2}}| = |\ot{\n\rls2}|$.
\item
Thus $|\head{\ot{\n\rls1}}| = |\head{\ot{\n\rls2}}| > 0$.
\item
Recall $\head{\ot{\n\rls1}} = \head{\n\rls1} \ne
\head{\n\rls2} = \head{\ot{\n\rls2}}$.
\item
Then $\head{\ot{\n\rls1}} \setd \head{\ot{\n\rls2}} \ne
\sete$.
\item
Select some $\n\lit1 \in \head{\ot{\n\rls1}} \setd
\head{\ot{\n\rls2}}$.
\item
Let $\n\rl1$ be the fact $(\n\lit1.)$ in
$\ot{\n\rls1} \setd\ot{\n\rls2}$.
\item
Since $\n\lits1$ is an answer set of $\n\p1$, we have
$\n\lit1 \in \n\lits1$.
\item
Recall $\n\lits1 \setsp \n\lits2$.
Then $\n\lit1 \in \n\lits2$.

\item
As $\n\lits2$ is an answer set of $\n\p2$, there exists
$\rl\in \n\p2$ which
supports $\n\lit1$ wrt $\n\lits2$.
\begin{enumerate}
\item
Case 1 of 2: there exists $\lit \in \posbody{\rl}$ where
$\lit \in \n\lits2 \setd \n\lits1$.
\begin{enumerate}
\item
Let minimal $\pr \in \prs\lit{\n\lits2}{\n\p2}$.
\item
By Lemma \ref{rule_in_P2}, there exists $\n\rl2 \in \pr$
where $\n\rl2 \in \n\p2 \setd \n\p1$.
\item
Then $\n\rl2 \in \ot{\n\rls2} \setd \ot{\n\rls1} \sets
\appl\pcr$.
\item
Let $h_{\n\lits2}(\n\rl2) = {\n\lit2} \in \head\pcr$.
\item
As $\pr$ is minimal, $\lit$ depends on $\n\lit2$.
\item
Recall $\n\lit1$ depends on $\lit$ in $\rl$.
\item
By transitivity, $\n\lit1$ depends on $\n\lit2$.
\end{enumerate}
\item
Case 2 of 2: $\posbody{\rl} \sets \n\lits1$.
We show this case is impossible.
\begin{enumerate}
\item
Subcase 1 of 2: $\rl \in \n\p1 \seti \n\p2$.
\begin{enumerate}
\item
Notice $\rl$ supports $\n\lit1$ wrt $\n\lits1$.
\item
By Lemma \ref{sole_supporting_rule}, since $\p$ is acyclic,
we have $\rl = \n\rl1$.
\item
However, $\rl \in \n\p2$ whereas
$\n\rl1 \in \n\p1 \setd \n\p2$, contradiction.
\end{enumerate}
\item
Subcase 2 of 2: $\rl \in \n\p2 \setd \n\p1$.
\begin{enumerate}
\item
So $\rl \in \ot{\n\rls2} \setd \ot{\n\rls1}$.
\item
Then $\rl$ is the fact $(\n\lit1.)$,
which is exactly $\n\rl1$.
\item
However, we selected $\n\rl1$ from
$\ot{\n\rls1} \setd \ot{\n\rls2}$
while $\rl \in \ot{\n\rls2}$, contradiction.
\end{enumerate}
\end{enumerate}
\end{enumerate}
\end{enumerate}

\end{proof}

%:hcf nondisjunctive
\begin{remark}
\label{hcf_nondisjunctive}

If a \cp{} program $\p$ is acyclic,
then there exists a nondisjunctive acyclic \cp{} program
$\ot\p$ equivalent to $\p$
\cite[page 73, Theorem 4.17]{hcfb}.

\end{remark}

%:last theorem
\begin{theorem}
[Antichain Property of CR-Independent Acyclic
\cp{} Programs]
\label{last_theorem}

Let $\p$ be an acyclic \cp{} program.
If $\p$ is cr-independent,
then $\p$ has antichain property.

\end{theorem}

\begin{proof}

By Remark \ref{hcf_nondisjunctive},
there exists a nondisjunctive acyclic \cp{} $\ot\p$
equivalent to $\p$.
By the contrapositive of Lemma \ref{last_lemma},
$\ot\p$ has antichain property.
Therefore, $\p$ has antichain property too.

\end{proof}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Conclusion}

We have found a reasonably weak syntactic condition
which guarantees that
a \cp{} program has antichain property:
the program being acyclic and cr-independent.
The future goal is to further relax
this sufficient condition to extend the class of
\cp{} programs known to have
this desired semantic property.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Acknowledgment}

We sincerely appreciate the significant guidance of \mg.
This paper includes his proofs of
Theorem \ref{antichain_a_prolog} and
Lemma \ref{answer_set_subprogram}.
We also thank Evgenii Balai for the
informative discussions.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{flushleft}

\newpage

\bibliography{bibl}

\end{document}

### 2017-04-18 paper/paper.tex
notations

@@
 
-\versions
-
-Revising my paper before submitting for publication.
-
-\bigskip
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
 \begin{center}
-
-{\Large \mytitle} \\ \medskip
-\vp \\
-\textit{\ttu}
-
+{\Large \mytitle}
 \end{center}
@@
 \begin{abstract}
-
-We study syntactic conditions which guarantee when
-a \cplong{} program has antichain property
-(no answer set is a proper subset of another).
-A notable such condition is that
-the program's dependency graph being acyclic
-and having no directed path from one cr-rule head literal
-to another.
-
+Game of Life.
 \end{abstract}
@@
 
-\newpage
-
 \begin{flushleft}
@@
 
-\section{Introduction}
+\section{Notations}
 
-\aplong{} (\ap) is a programming language
-for knowledge representation and reasoning.
-Every \ap{} program has antichain property:
-no answer set is a proper subset of another.
-This property is desirable,
-because we want minimal solutions
-to planning and diagnostic problems.
-
-\bigskip
-
-\cplong{} (\cp) extends \ap{} with cr-rules.
-In \cp, indirect exceptions can be elegantly encoded.
-However, there exist \cp{} programs
-without antichain property.
-We investigate some syntactic conditions
-guaranteeing that a \cp{} program
-has this desired semantic property.
-Such conditions are specified in Theorem \ref{last_theorem}
-(most notable) as well as
-Theorem \ref{antichain_a_prolog},
-Corollary \ref{one_cr_rule},
-and Propositions \ref{unique_cr_literals} \&
-\ref{same_abductive_support_heads}.
+For each $n \in \Zplus$:
+\begin{enumerate}
+\item let $\sp{n} = \Ftwo ^ {\Zn ^ 2}$
+\item let $\l: \sp{n+2} \to \sp{n}$
+\end{enumerate}
 
@@
 
-\section{Preliminary Results}
+\section{Results}
 
-\subsection{Background}
+\begin{conjecture}
 
-Note: the complete specifications of \ap{} and \cp{}
-can be found in \cite[Sections 2.1, 2.2, 5.5]{krb}.
-We focus on the \cp{} variant in which
-minimality of abductive supports is based on cardinality.
-
-\begin{definition}
-[Regular Rule]
-
-A \textdef{regular rule} has the form:
-$$\regrule$$
-where each $\lit_\ind$ is a ground literal and
-$0 \le \nhl \le \nbl \le \nel$.
-
-\end{definition}
-
-\begin{definition}
-[CR-Rule]
-
-Similar to a regular rule,
-a \textdef{cr-rule} has the form:
-$$l_0 \whencr
-l_1, \ldots, l_\nbl,\
-not\ l_{\nbl + 1}, \ldots, not\ l_\nel.$$
-
-\end{definition}
-
-\begin{definition}
-[\ap{} Program]
-
-An \textdef{\ap{} program} is a finite set of
-regular rules.
-
-\end{definition}
-
-\begin{definition}
-[\cp{} Program]
-
-A \textdef{\cp{} program} is a finite set of
-regular rules and cr-rules.
-Notations: $\preg$ and $\pcr$ denote
-the corresponding subsets of regular rules and cr-rules.
-
-\end{definition}
-
-\begin{definition}
-[Applications of CR-Rules]
-
-Let $\rl$ be a cr-rule.
-Then the \textdef{application} $\appl\rl$ is
-the regular rule obtained from $\rl$ by
-replacing $\whencr$ with $\when$.
-If $\rls$ is a set of cr-rules, then let
-$\appl\rls = \set{\appl\rl : \rl \in \rls}$.
-When $\rls$ is a subset of a \cp{} program $\p$,
-let $\pappld\rls$.
-
-\end{definition}
-
-\begin{definition}
-[Antichain Property]
-
-Let $\p$ be a \cp{} program.
-We say $\p$ has \textdef{antichain property} if:
-for all answer sets $\n\lits1$ and $\n\lits2$ of $\p$,
-we have $\n\lits1 \sets \n\lits2 \impl \n\lits1 = \n\lits2$.
-
-\end{definition}
-
-\begin{example}
-[\cp{} Program without Antichain Property]
-
-Consider the following program:
-\begin{gather*}
-a. \\
-\neg a \when \negd{b}, \negd{c}. \\
-b \when c. \\
-b \whencr. \tag{$\n\rl1$} \\
-c \whencr. \tag{$\n\rl2$}
-\end{gather*} \\
-This program has answer sets $\n\lits1 = \{a, b\}$ and
-$\n\lits2 = \{a, b, c\}$.
-Observe that $\n\lits1 \setsp \n\lits2$ (proper subset).
-The corresponding abductive supports are
-$\n\rls1 = \set{\n\rl1}$ and $\n\rls2 = \set{\n\rl2}$.
-
-\end{example}
-
-\subsection{Up to One CR-Rule}
-
-\begin{remark}
-\label{vacuous_antichain}
-
-Every inconsistent \cp{} program vacuously has
-antichain property.
-So only consistent programs are of interest.
-
-\end{remark}
-
-\begin{definition}
-[Reduct]
-
-Let $\rls$ be a set of regular rules and $\lits$ be a
-consistent set of literals.
-We write $\reduct{\rls}{\lits}$ for the \textdef{reduct} of
-$\rls$ wrt $\lits$.
-
-\end{definition}
-
-\begin{lemma}
-\label{reducts_subset}
-
-Let $\p$ be an \ap{} program.
-Let $\n\lits1$ and $\n\lits2$ be consistent sets of
-literals.
-If $\n\lits1 \sets \n\lits2$, then
-$\reduct{\p}{\n\lits2} \sets \reduct{\p}{\n\lits1}$.
-
-\end{lemma}
-
-\begin{proof}
-
-Assume $\reduct{\p}{\n\lits2}$ has an arbitrary rule $\rl$:
-$$\regrulenodefneg$$
-The corresponding rule in $\p$ is:
-$$\regrule$$
-For each $\ind$ in $\set{\nbl + 1, \ldots, \nel}$, we have
-$l_\ind \notin \n\lits2$,
-so $l_\ind \notin \n\lits1$ (as $\n\lits1 \sets \n\lits2$).
-Therefore, $\rl$ is also a rule in $\reduct{\p}{\n\lits1}$.
-
-\end{proof}
-
-%:antichain A-Prolog
-\begin{theorem}
-[Antichain Property of \ap{} Programs, proved by \mg]
-\label{antichain_a_prolog}
-
-Let $\p$ be an \ap{} program.
-Let $\n\lits1 \sets \n\lits2$ be answer sets of $\p$.
-Then $\n\lits1 = \n\lits2$.
-
-\end{theorem}
-
-\begin{proof}
-
-We will show $\n\lits2 \sets \n\lits1$.
-
-\begin{enumerate}
-\item
-First, $\n\lits2$ is an answer set of
-$\reduct{\p}{\n\lits2}$.
-So $\n\lits2$ is a minimal (wrt set inclusion)
-consistent set of literals which
-satisfies $\reduct{\p}{\n\lits2}$.
-We shall prove $\n\lits2 \sets \n\lits1$ by showing
-$\n\lits1$ also satisfies $\reduct{\p}{\n\lits2}$.
-\item
-By \ref{reducts_subset}, we have $\reduct{\p}{\n\lits2}
-\sets\reduct{\p}{\n\lits1}$.
-Because $\n\lits1$ satisfies $\reduct{\p}{\n\lits1}$,
-we know $\n\lits1$ also satisfies $\reduct{\p}{\n\lits2}$.
-\end{enumerate}
-
-\end{proof}
-
-\begin{definition}
-[Equivalence of \cp{} Programs]
-
-Let $\n\p1$ and $\n\p2$ be \cp{} programs.
-We say $\n\p1$ and $\n\p2$ are \textdef{equivalent},
-denoted by $\n\p1 \equi \n\p2$, when
-$\lits$ is an answer set of $\n\p1$ iff $\lits$ is an
-answer set of $\n\p2$ for every consistent set of literals
-$\lits$.
-\end{definition}
-
-\begin{remark}
-\label{consistent_p_reg}
-
-Let $\p$ be a \cp{} program.
-If $\preg$ is consistent, then $\p$ is equivalent to
-$\preg$, which has antichain property due to Theorem
-\ref{antichain_a_prolog}.
-The interesting case is when $\preg$ is inconsistent.
-
-\end{remark}
-
-\begin{corollary}
-\label{one_cr_rule}
-
-Let $\p$ be a \cp{} program where \inconspreg{}.
-If $\p$ has only one cr-rule, then $\p$ has
-antichain property.
-
-\end{corollary}
-
-\begin{proof}
-
-Assume $\pcr = \set\rl$ for some cr-rule $\rl$.
-Then $\p$ is equivalent to the \ap{} program
-$\pappld{\set\rl}$.
-Simply apply Theorem \ref{antichain_a_prolog} to
-$\pappl{\set\rl}$.
-
-\end{proof}
-
-\subsection{Unique CR-Literals}
-
-\begin{definition}
-[Useless Regular Rule]
-
-Let $\p$ be an \ap{} program containing some rule $\rl$.
-For an answer set $\lits$ of $\p$, we say $\rl$ is
-\textdef{useless} wrt $\lits$ if $\lits$ is an answer set
-of $\p \setd \set\rl$.
-
-\end{definition}
-
-\begin{definition}
-[Regular Rule Firing]
-
-Given a regular rule $\rl$ and a consistent set of literals
-$\lits$, we say $\rl$ \textdef{fires} wrt $\lits$ if
-$\lits$ satisfies the body of $\rl$.
-
-\end{definition}
-
-\begin{lemma}
-\label{unreduced_rule_fires_iff}
-
-Let $\rl$ be a regular rule and $\lits$ be a
-consistent set of literals.
-Assume $\reduct{\set\rl}\lits = \set{\ot\rl}$ for some
-\dnf{} rule $\ot\rl$.
-Then $\rl$ fires iff $\ot\rl$ fires, wrt $\lits$.
-
-\end{lemma}
-
-\begin{proof}
-
-The two rules are:
-\begin{gather*}
-\regrule \tag{$\rl$} \\
-\regrulenodefneg \tag{$\ot\rl$}
-\end{gather*} \\
-By construction of $\ot\rl$ from $\rl$,
-we know $\n\lit\ind \not\in \lits$ for all $\ind \in
-\set{\nbl + 1, \ldots, \nel}$.
-Then $\rl$ fires wrt $\lits$ iff
-$\n\lit\ind \in \lits$ for all
-$\ind \in \set{\nhl + 1, \ldots, \nbl}$ iff
-$\ot\rl$ fires wrt $\lits$.
-
-\end{proof}
-
-\begin{remark}
-\label{superset_fires}
-
-Let $\rl$ be a regular \dnf{} rule and
-$\n\lits1 \sets \n\lits2$ be consistent sets of literals.
-If $\rl$ fires wrt $\n\lits1$, then $\rl$ fires wrt
-$\n\lits2$.
-
-\end{remark}
-
-\begin{lemma}
-\label{useless_unless_fires}
-
-Let $\p$ be an \ap{} program containing some rule $\rl$.
-Let $\lits$ be an answer set of $\p$.
-If $\rl$ does not fire, then $\rl$ is useless, wrt $\lits$.
-
-\end{lemma}
-
-\begin{proof}
-
-Let $\n\p1 = \reduct\p\lits$ and
-$\n\p2 = \reduct{(\p \setd \set\rl)}\lits$.
-We know $\lits$ is an answer set of $\n\p1$.
-We will prove $\lits$ is an answer set of $\n\p2$.
-
-\begin{enumerate}
-
-\item
-First, $\lits$ satisfies $\n\p1$. Notice
-$\n\p2 \sets \n\p1$.
-Then $\lits$ satisfies $\n\p2$.
-
-\item
-Assume some consistent set of literals
-$\ot\lits \sets \lits$ also satisfies $\n\p2$.
-We shall show $\ot\lits = \lits$.
-\begin{enumerate}
-\item
-Case 1 of 2: $\reduct{\set\rl}\lits = \sete$.
-Then $\n\p1 = \n\p2$, so $\ot\lits$ satisfies $\n\p1$.
-\item
-Case 2 of 2: $\reduct{\set\rl}\lits = \set{\ot\rl}$ for
-some \dnf{} rule $\ot\rl$.
-Recall that we hypothesized $\rl$ does not fire wrt
-$\lits$. By Lemma \ref{unreduced_rule_fires_iff}, we know
-$\ot\rl$ does not fire wrt $\lits$.
-Since $\ot\lits \sets \lits$, using the contrapositive of
-Remark \ref{superset_fires},
-we deduce that $\ot\rl$ does not fire wrt $\ot\lits$.
-Then $\ot\lits$ vacuously satisfies $\ot\rl$.
-So $\ot\lits$ satisfies $\n\p1 = \n\p2 \setu \set{\ot\rl}$.
-\end{enumerate}
-In both cases, $\ot\lits$ satisfies $\n\p1$.
-As $\lits$ is an answer set of $\n\p1$, due to minimality,
-we know $\lits \sets \ot\lits$.
-Since we assumed $\ot\lits \sets \lits$, we can now
-conclude that $\ot\lits = \lits$.
-
-\item
-We have shown that $\lits$ is a minimal consistent set of
-literals which satisfies $\n\p2$.
-Hence, $\lits$ is an answer set of $\n\p2$.
-
-\end{enumerate}
-
-\end{proof}
-
-\begin{lemma}
-\label{cr_rule_not_useless}
-
-Let $\p$ be a \cp{} program.
-Let $\lits$ be an answer set of $\p$ and $\rls$ be a
-corresponding abductive support.
-Let cr-rule $\rl \in \rls$.
-Then $\appl\rl$ is not useless wrt $\lits$.
-
-\end{lemma}
-
-\begin{proof}
-
-By way of contradiction, assume $\appl\rl$ is useless wrt
-$\lits$.
-Let $\pappld\rls$.
-Then $\lits$ is an answer set of
-$\pappl\rls \setd \set{\appl\rl}$,
-whereas this program is precisely $\pappld{\ot\rls}$ with
-$\ot\rls = \rls \setd \set\rl$.
-So $\pappl{\ot\rls}$ is consistent.
-Since $\rls$ is a minimal (wrt cardinality) set of cr-rules
-whose applications make $\p$ consistent,
-we have $|\rls| \le |\ot\rls|$.
-However, $|\ot\rls| = |\rls| - 1$
-(recall $\ot\rls = \rls \setd \set\rl$), contradiction.
-
-\end{proof}
-
-\begin{lemma}
-\label{abductive_support_fires}
-
-Let $\p$ be a \cp{} program.
-Let $\lits$ be an answer set of $\p$ and $\rls$ be a
-corresponding abductive support.
-Let cr-rule $\rl \in \rls$.
-Then the application $\appl\rl$ fires wrt $\lits$.
-
-\end{lemma}
-
-\begin{proof}
-
-First, $\lits$ is an answer set of $\pappld\rls$.
-By way of contradiction, assume there exists some cr-rule
-$\rl \in \rls$ such that
-$\appl\rl$ does not fire wrt $\lits$.
-By Lemma \ref{useless_unless_fires}, $\appl\rl$ is useless
-wrt $\lits$.
-However, by \ref{cr_rule_not_useless}, $\appl\rl$ is not
-useless wrt $\lits$, contradiction.
-
-\end{proof}
-
-\begin{definition}
-[Head]
-
-If $\rl$ is a rule, then let $\head\rl$ denotes the set of
-literals which appear in the head of $\rl$.
-If $\rls$ is a set of rules, then let
-$\head\rls = \bigcup_{\rl \in \rls} \head\rl$.
-
-\end{definition}
-
-%:supported literal
-\begin{definition}
-[Supported Literal]
-
-Let $\rl$ be a regular rule,
-$\lit$ be a literal,
-and $\lits$ be a consistent set of literals.
-We say $\lit$ is \textdef{supported} by $\rl$ wrt $\lits$
-if all of the following hold:
-\begin{enumerate}
-\item
-$\rl$ fires wrt $\lits$
-\item
-$\head\rl \seti \lits = \set\lit$
-\end{enumerate}
-\cite[page 43, Proposition 2.2.1]{krb}
-
-\end{definition}
-
-\begin{proposition}
-\label{unique_cr_literals}
-
-Let $\p$ be a \cp{} program.
-If the literal in the head of each cr-rule does not appear
-in the head of any other rule,
-then $\p$ has antichain property.
-
-\end{proposition}
-
-\begin{proof}
-
-Let $\n\lits1$ and $\n\lits2$ be answer sets of $\p$.
-Assume $\n\lits1 \sets \n\lits2$.
-We will show $\n\lits1 = \n\lits2$.
-
-\begin{enumerate}
-
-\item
-Let $\n\rls1$ and $\n\rls2$ respectively be abductive
-supports for $\n\lits1$ and $\n\lits2$.
-We first prove $\n\rls1 \sets \n\rls2$.
-Let $\rl$ be an arbitrary cr-rule in $\n\rls1$.
-By Lemma \ref{abductive_support_fires},
-$\rl$ fires wrt $\n\lits1$, and
-$\n\lits1$ satisfies $\head\rl = \set{\lit}$
-where $\lit$ is a literal.
-So $\lit \in \n\lits1$, then $\lit \in \n\lits2$
-(as $\n\lits1 \sets \n\lits2$).
-By the hypothesized syntactic condition, $\rl$ is the sole
-rule in $\p$ whose head contains $\lit$.
-Then only $\rl$ can support $\lit$ wrt $\n\lits2$.
-So $\rl \in \n\rls2$.
-
-\item
-Now that we showed $\n\rls1 \sets \n\rls2$,
-recall $|\n\rls1| = |\n\rls2|$,
-as both are abductive supports.
-Then $\n\rls1 = \n\rls2$, since they are finite sets.
-Consequently, $\pappld{\n\rls1}$ equals $\pappld{\n\rls2}$.
-So $\n\lits1$ and $\n\lits2$ are answer sets of the same
-\ap{} program.
-By Theorem \ref{antichain_a_prolog}, $\n\lits1 = \n\lits2$.
-
-\end{enumerate}
-
-\end{proof}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Main Results}
-
-\subsection{Dependency Graphs}
-
-\begin{definition}
-[Positive Body of Rule]
-
-Let $\rl$ be a rule.
-The \textdef{positive body} of $\rl$,
-denoted by $\posbody\rl$,
-is the set of literals in the body of $\rl$ which are
-\dnf.
-
-\end{definition}
-
-\begin{definition}
-[Dependency Graph]
-
-Let $\p$ be a \cp{} program.
-Let $\g\p$ be a graph whose vertices are literals of $\p$.
-For each pair of vertices $\n\lit1$ and $\n\lit2$ of
-$\g\p$, there is a directed edge to $\n\lit1$ from
-$\n\lit2$ if $\p$ has some rule $\rl$ where
-$\n\lit1 \in \head\rl$ and $\n\lit2 \in \posbody\rl$.
-We say $\g\p$ is the \textdef{dependency graph} of $\p$.
-Note: a self-loop forms a directed cycle.
-
-\end{definition}
-
-\begin{remark}
-[Answer Set of Acyclic Program]
-\label{acyclic_answer_set}
-
-Let $\p$ be an acyclic \ap{} program and $\lits$ be a
-consistent set of literals.
-Then $\lits$ is an answer set of $\p$ iff every literal in
-$\lits$ is supported by a rule in $\p$ wrt $\lits$
-\cite[page 58, Theorem 2.7]{hcfb}.
-
-\end{remark}
-
-%:ex self-loop
-\begin{example}
-[Self-Loop Forming Cycle]
-
-To the contrary, assume a self-loop does not form a cycle.
-Consider this \ap{} program:
-\begin{gather*}
-\lit \when \lit. \tag{$\rl$}
-\end{gather*}
-Let $\lits = \set{\lit}$.
-Notice that $\lit$ is supported by $\rl$ wrt $\lits$.
-However, $\lits$ is not an answer set of $\p$.
-Then Remark \ref{acyclic_answer_set} is wrong,
-contradiction.
-
-\end{example}
-
-\begin{definition}
-[Head-Cycle]
-
-Let $\p$ be a \cp{} program with dependency graph $\g\p$.
-Let $\cy$ be a cycle in $\g\p$.
-Assume:
-\begin{enumerate}
-\item
-vertices $\n\lit1$ and $\n\lit2$ are in $\cy$
-\item
-there exists $\rl \in \p$ where
-$\n\lit1$ and $\n\lit2$ are in $\head\rl$
-\end{enumerate}
-Then $\cy$ is called a \textdef{\hc} in $\p$.
-
-\end{definition}
-
-\begin{definition}
-[Dependent Literals]
-
-Let $\p$ be a \cp{} program with dependency graph $\g\p$.
-Let $\n\lit1$ and $\n\lit2$ be two literals appearing in
-$\p$.
-We say $\n\lit1$ \textdef{depends} on $\n\lit2$ if
-$\g\p$ has a directed path to $\n\lit1$ from $\n\lit2$.
-
-\end{definition}
-
-\begin{definition}
-[CR-Literal]
-
-Let $\p$ be \cp{} program with cr-rule $\rl$ where
-$\head\rl = \set\lit$.
-We say $\lit$ is a \textdef{cr-literal} of $\p$.
-
-\end{definition}
-
-\begin{definition}
-[CR-Independence]
-
-Let $\p$ be a \cp{} program.
-Then $\p$ is \textdef{cr-independent} if
-$\n\lit1$ does not depend on $\n\lit2$
-for all cr-literals $\n\lit1$ and $\n\lit2$.
-
-\end{definition}
-
-\subsection{Same Abductive Support Heads}
-
-\begin{remark}
-
-Let $\p$ be a \cp{} program with some answer set $\lits$.
-Then $\lits \sets \head\p$.
-
-\end{remark}
-
-\begin{remark}
-\label{empty_reduct_unless_fires}
-
-Let $\rl$ be a regular rule and $\lits$ be a consistent set
-of literals.
-If $\rl$ fires wrt $\lits$, then
-$\reduct{\set\rl}\lits \ne \sete$.
-
-\end{remark}
-
-\begin{remark}
-\label{nonempty_reduced_cr_rule}
-
-Let $\p$ be a \cp{} program with some answer set $\lits$
-and a corresponding abductive support $\rls$.
-Let cr-rule $\rl \in \rls$. Then
-$\reduct{\set{\appl\rl}}\lits \ne \sete$.
-(Use Lemma \ref{abductive_support_fires} and Remark
-\ref{empty_reduct_unless_fires}.)
-
-\end{remark}
-
-\begin{example}
-
-Consider an inconsistent \ap{} program $\p$:
-$$\lit \when \negd\lit.$$
-Let $\lits = \set\lit$.
-Notice $\lits$ is a minimal consistent set of literals
-which satisfies $\p$.
-However, $\lits$ is not an answer set of $\p$, because
-$\lits$ nonminimally satisfies $\reduct\p\lits = \sete$.
-(Note that $\ot\lits = \sete$ satisfies neither $\p$ nor
-$\reduct\p{\ot\lits} = \set{\lit.}$.)
-
-\end{example}
-
-\begin{example}
-
-Consider a consistent \cp{} program $\p$:
-\begin{gather*}
-\when \negd {\n\lit1}, \negd {\n\lit2}. \\
-\n\lit1 \whencr \negd {\n\lit2}. \tag{$\rl$}
-\end{gather*} \\
-Then $\rls = \set\rl$ is an abductive support of $\p$.
-Indeed, let $\pappld\rls$,
-then $\lits = \set{\n\lit1}$ is an answer set of
-$\reduct{\pappl\rls}\lits = \set{\n\lit1}$.
-Notice $\ot\lits = \set{\n\lit2}$ satisfies $\pappl\rls$,
-but $\n\lit1 \not\in \ot\lits$.
-
-\end{example}
-
-\begin{lemma}
-\label{intersection_satisfies}
-
-Let $\p$ be a nondisjunctive \dnf{} \ap{} program.
-If consistent sets of literals $\n\lits1$ and $\n\lits2$
-satisfy $\p$,
-then $\n\lits0 = \n\lits1 \seti \n\lits2$ also satisfies
-$\p$.
-
-\end{lemma}
-
-\begin{proof}
-
-Let $\rl$ be a rule in $\p$.
-Assume $\rl$ fires wrt $\n\lits0$.
-Then $\rl$ also fires wrt $\n\lits1$ and $\n\lits2$
-(as $\p$ is \dnf).
-So $\n\lits1$ and $\n\lits2$ satisfy $\head\rl = \set\lit$
-(since $\p$ is nondisjunctive).
-Thus $\lit$ is in $\n\lits1$, $\n\lits2$, and $\n\lits0$.
-
-\end{proof}
-
-\begin{lemma}
-[Proved by \mg]
-\label{answer_set_subprogram}
-
-Let $\p$ be a nondisjunctive \dnf{} \ap{} program.
-Assume $\p$ has rules $\n\rl1 \ne \n\rl2$ such that
-$\head{\n\rl1} = \head{\n\rl2}$.
-Let $\n\p0 = \p \setd \set{\n\rl1, \n\rl2}$,
-$\n\p1 = \n\p0 \setu \set{\n\rl1}$,
-and $\n\p2 = \n\p0 \setu \set{\n\rl2}$.
-If $\lits$ is an answer set of $\p$, then $\lits$ is also
-an answer set of either $\n\p1$ or $\n\p2$.
-
-\end{lemma}
-
-\begin{proof}
-
-To the contrary, assume $\lits$ is an answer set of neither
-$\n\p1$ nor $\n\p2$.
-Still, $\lits$ satisfies both $\n\p1$ and $\n\p2$
-(as $\lits$ satisfies $\p$).
-So there exist two proper subsets of $\lits$, say
-$\n\lits1$ and $\n\lits2$,
-which respectively satisfy $\n\p1$ and $\n\p2$
-(the programs are \dnf{}).
-
-\begin{enumerate}
-
-\item
-Case 1 of 2: either $\n\rl1$ fires wrt $\n\lits1$, or
-$\n\rl2$ fires wrt $\n\lits2$.
-WOLOG, assume the former. Then $\n\lits1$ satisfies
-$\head{\n\rl1} = \head{\n\rl2}$.
-So $\n\lits1$ also satisfies both the rule $\n\rl2$ and the
-program $\p = \n\p1 \setu \set{\n\rl2}$.
-Recall that $\lits$ is an answer set of $\p$ whereas
-$\n\lits1 \setsp \lits$, contradiction.
-
-\item
-Case 2 of 2: neither $\n\rl1$ fires wrt $\n\lits1$, nor
-$\n\rl2$ fires wrt $\n\lits2$.
-So neither $\n\rl1$ nor $\n\rl2$ fires wrt
-$\n\lits0 = \n\lits1 \seti \n\lits2$
-(the rules are \dnf).
-Then $\n\lits0$ vacuously satisfies $\n\rl1$ and $\n\rl2$.
-Because $\n\lits1$ and $\n\lits2$ satisfy $\n\p0$,
-by \ref{intersection_satisfies},
-$\n\lits0$ satisfies $\n\p0$ too.
-Therefore, $\n\lits0$ satisfies
-$\p = \n\p0 \setu \set{\n\rl1, \n\rl2}$.
-But $\lits$ is an answer set of $\p$, and
-$\n\lits0 \setsp \lits$, contradiction.
-
-\end{enumerate}
-
-\end{proof}
-
-%:diff cr-literals
-\begin{lemma}
-\label{diff_cr_literals}
-
-Let $\p$ be a nondisjunctive \cp{} program with some
-abductive support $\rls$.
-Then for all cr-rules $\n\rl1$ and $\n\rl2$ in $\rls$,
-we have
-$\head{\n\rl1} = \head{\n\rl2} \impl \n\rl1 = \n\rl2$.
-
-\end{lemma}
-
-\begin{proof}
-
-By way of contradiction, assume there exist cr-rules
-$\n\rl1\ne \n\rl2$ in $\rls$ where
-$\head{\n\rl1} = \head{\n\rl2}$.
-Some notations:
-\begin{enumerate}
-\item
-Let $\n\rls1 = \rls \setd \set{\n\rl2}$ and
-$\n\rls2 = \rls \setd \set{\n\rl1}$.
-\item
-Let $\n\p1 = \applp{\n\rls1}$ and
-$\n\p2 = \applp{\n\rls2}$.
-\item
-Let $\lits$ be an answer set of $\p$ wrt $\rls$.
-\item
-Let $\n\p a = \reduct{\n\p1}\lits$ and
-$\n\p b = \reduct{\n\p2}\lits$.
-Note that by \ref{nonempty_reduced_cr_rule},
-$\reduct{\set{\appl{\n\rl1}}}\lits = \set{\ot{\n\rl1}}$ and
-$\reduct{\set{\appl{\n\rl2}}}\lits = \set{\ot{\n\rl2}}$ for
-some \dnf{} rules $\ot{\n\rl1}$ and $\ot{\n\rl2}$.
-\end{enumerate}
-
-By \ref{answer_set_subprogram}, $\lits$ is an answer set of
-either $\n\p a$ or $\n\p b$.
-WOLOG, assume the former.
-Then $\lits$ is an answer set of $\n\p1$.
-So $\n\rls1$ is an abductive support of $\p$,
-but $|\n\rls1| < |\rls|$, contradiction.
-
-\end{proof}
-
-%:sole supporting rule
-\begin{lemma}
-\label{sole_supporting_rule}
-
-Let $\p$ be an acyclic \cp{} program having some answer set
-$\lits$ wrt an abductive support $\rls$.
-Let cr-rule $\rl \in \rls$ where $\head\rl = \set\lit$.
-Then $\appl\rl$ is the only rule in $\pappld\rls$ which
-supports $\lit$ wrt $\lits$.
-
-\end{lemma}
-
-\begin{proof}
-
-By way of contradiction, assume $\lit$ is also supported by
-a rule $\ot\rl \ne \appl\rl$ in $\pappl\rls$.
-Let $\ot\rls = \rls \setd \set{\rl}$ and
-$\ot\p = \applp{\ot\rls}$.
-We will prove $\lits$ is an answer set of $\ot\p$:
-\begin{enumerate}
-\item
-First, $\lits$ satisfies $\ot\p \sets \pappl\rls$.
-\item
-Let $\ot\lit$ be an arbitrary literal in $\lits$. We show
-$\ot\lit$ is supported wrt $\lits$ by some rule in $\ot\p$.
-Recall that $\lits$ is an answer set of $\pappl\rls$.
-By \ref{acyclic_answer_set}, $\ot\lit$ is supported wrt
-$\lits$ by some rule $\n\rl0$ in $\pappl\rls$.
-\begin{enumerate}
-\item
-Case 1 of 2: $\n\rl0 = \appl\rl$.
-Recall $\head\rl = \set\lit$.
-Then $\ot\lit = \lit$.
-Notice $\ot\rl$ also supports $\ot\lit$ wrt $\lits$, and
-$\ot\rl \in \ot\p$.
-\item
-Case 2 of 2: $\n\rl0 \ne \appl\rl$.
-Then $\n\rl0 \in \ot\p$.
-\end{enumerate}
-\end{enumerate}
-So $\ot\p$ is consistent, and $\ot\rls$ is an abductive
-support of $\p$.
-But $|\ot\rls| < |\rls|$, contradiction.
-
-\end{proof}
-
-\begin{definition}
-[Factified Rule]
-
-Let $\rl$ be a regular rule.
-Let $\factify\rl$ denote the \textdef{factified rule}
-obtained from $\rl$ by dropping its body.
-If $\rls$ is a set of rules, then let
-$\factify\rls = \set{\factify\rl : \rl \in \rls}$.
-
-\end{definition}
-
-%:factify answer set
-\begin{lemma}
-\label{factify_answer_set}
-
-Let $\p$ be a \cp{} program with answer set $\lits$ and
-corresponding abductive support $\rls$.
-Then $\lits$ is an answer set of
-$\ot\p = \preg \setu \factify{\appl\rls}$.
-
-\end{lemma}
-
-\begin{proof}
-We prove $\lits$ is a minimal consistent set of literals
-which satisfies $\reduct{\ot\p}\lits$:
-\begin{enumerate}
-\item
-Let $\pappld\rls$.
-Note that $\head\rls \sets \lits$ as $\lits$ is an answer
-set of $\pappl\rls$.
-Then $\lits$ satisfies
-$\reduct{\ot\p}\lits =
-\reduct{(\preg)}{\lits} \setu \factify{\appl\rls}$.
-\item
-Assume some $\ot\lits \sets \lits$ also satisfies
-$\reduct{\ot\p}\lits$.
-We know $\head\rls \sets \ot\lits$.
-Then $\ot\lits$ satisfies
-$\reduct{(\pappl\rls)}\lits =
-\reduct{(\preg)}\lits \setu \reduct{(\appl\rls)}\lits$.
-So $\lits \sets \ot\lits$
-(as $\lits$ is an answer set of
-$\pappl\rls$). Therefore $\ot\lits = \lits$.
-\end{enumerate}
-
-\end{proof}
-
-%:same abductive support heads
-\begin{proposition}
-\label{same_abductive_support_heads}
-
-Let $\p$ be a \cp{} program.
-Then $\p$ has antichain property if
-$\head{\n\rls1} = \head{\n\rls2}$ for
-all abductive supports $\n\rls1$ and $\n\rls2$ of $\p$.
-
-\end{proposition}
-
-\begin{proof}
-
-Let $\n\lits1$ and $\n\lits2$ be arbitrary answer sets of
-$\p$ corresponding to
-some abductive supports $\n\rls1$ and $\n\rls2$.
-By \ref{factify_answer_set}, $\n\lits1$ and $\n\lits2$ are
-respectively answer sets of
-$\preg \setu \factify{\appl{\n\rls1}}$ and
-$\preg \setu \factify{\appl{\n\rls2}}$,
-which are the same \ap{} program because
-$\head{\n\rls1} = \head{\n\rls2}$.
-By Theorem \ref{antichain_a_prolog},
-$\n\lits1 \sets \n\lits2 \impl \n\lits1 = \n\lits2$.
-
-\end{proof}
-
-\subsection{CR-Independence and Acyclicity}
-
-%:proof of literal
-\begin{definition}
-[Proof of Literal]
-
-Let $\p$ be an \ap{} program,
-$\lits$ be a consistent set of literals,
-and $\lit$ be a literal.
-A \textdef{proof} of $\lit$ wrt $\lits$ in $\p$ is
-a nonempty sequence of rules
-$\pr = \n\rl1, \ldots, \n\rl n$ in $\p$ such that:
-\begin{enumerate}
-\item
-for each rule $\n\rl i$, there is a (sole) literal
-$\ot\lit$ supported by $\rl$ wrt $\lits$;
-let $h_\lits(\rl)$ denote $\ot\lit$
-\item
-$\lit = h_\lits(\n\rl n)$
-\item
-$\posbody{\n\rl1} = \sete$
-%:hcf error
-\footnote
-{Their original definition states: $\n\rl1$ is a fact.
-However, there is an error in their Lemma B.5 on page 83.
-Consider an acyclic \ap{} program $\set{a \when \negd b.}$
-with answer set $\set{a}$.}
-\item
-for each rule $\n\rl i$,
-every literal in $\posbody{\n\rl i}$ is $h_\lits(\n\rl j)$
-for some $j < i$
-\end{enumerate}
-\cite[page 57]{hcfb}
-
-\end{definition}
-
-\begin{definition}
-
-Additional notations:
-\begin{enumerate}
-\item
-$\prs{\lit}{\lits}{\p}$ denotes the set of all proofs $\pr$
-of $\lit$ wrt $\lits$ in $\p$
-\item
-$h_\lits(\pr)$ denotes $\set{h_\lits(\rl) : \rl \in \pr}$
-\item
-$\posbody\pr$ denotes $\set{\posbody\rl : \rl \in \pr}$
-\end{enumerate}
-
-\end{definition}
-
-\begin{remark}
-
-Let $\pr = \rlseq1n \in \prs\lit\lits\p$.
-We adopt the convention that the rules in $\pr$ are
-pairwise distinct.
-Indeed, if there were $\n\rl i = \n\rl j$ where
-$i < j$, then $\ot\pr =
-\rlseq1{j - 1}, \rlseq{j + 1}n \in \prs\lit\lits\p$,
-so $\n \rl j$ would be redundant.
-
-\end{remark}
-
-\begin{remark}
-
-Let $\p$ be a \hcf{} \ap{} program with answer set $\lits$.
-Then each literal in $\lits$ has a proof wrt $\lits$ in
-$\p$ \cite[page 57]{hcfb}.
-
-\end{remark}
-
-\begin{definition}
-[Rank of Literal]
-
-Let $\p$ be a \hcf{} \ap{} program and
-$\lits$ be a consistent set of literals.
-The \textdef{rank} of a literal $\lit$ wrt $\lits$ in $\p$,
-denoted by $\rkt\lit\lits\p$, is
-$min\set{|\pr| : \pr \in \prs\lit\lits\p}$.
-
-\end{definition}
-
-\begin{definition}
-[Ranking Function]
-
-Let:
-\begin{enumerate}
-\item
-$\p$ be a \hcf{} \ap{} program
-\item
-$\lits$ be an answer set of $\p$
-\item
-function $\rkn : \lits \to \mathbb{N}$
-\end{enumerate}
-
-Then $\rkn$ is the \textdef{ranking function}
-wrt $\lits$ in $\p$ if $\rku\lit = \rkt\lit\lits\p$
-for all $\lit \in \lits$.
-
-\end{definition}
-
-\begin{definition}
-[Normal Proof of Literal]
-
-Let:
-\begin{enumerate}
-\item
-$\p$ be a \hcf{} \ap{} program
-\item
-$\lits$ be an answer set of $\p$
-\item
-$\lit \in \lits$
-\item
-$\pr \in \prs\lit\lits\p$
-\item
-$\rkn$ be the ranking function wrt $\lits$ in $\p$
-\end{enumerate}
-
-We say $\pr$ is a \textdef{normal proof} if
-for all $\rl \in \pr$ and $\ot\lit \in \posbody\rl$,
-we have $\rku{\ot\lit} < \rku{h_\lits(\rl)}$.
-
-\end{definition}
-
-\begin{remark}
-
-Let:
-\begin{enumerate}
-\item
-$\p$ be a \hcf{} \ap{} program
-\item
-$\lits$ be an answer set of $\p$
-\item
-$\rkn$ be the ranking function wrt $\lits$ in $\p$
-\item
-$\lit \in \lits$
-\item
-normal $\pr = \rlseq1n \in \prs\lit\lits\p$
-\item
-$\n\rl i \in \pr$
-\item
-$\n\lit i \in \posbody{\n\rl i}$.
-\end{enumerate}
-
-Then:
-\begin{enumerate}
-\item
-$\rku{\n\lit i} < \rku\lit$
-\item
-$\rlseq1i$ is a normal proof of $h_\lits(\n\rl i)$
-\end{enumerate}
-
-\end{remark}
-
-%:ex nonminimal subproof
-\begin{example}
-[Nonminimal Subproof of Minimal Proof]
-
-Consider this acylic \ap{} program $\p$:
-\begin{gather}
-a \when b, c. \\
-b \when c1x. \\
-c \when c1x. \\
-c1x \when c1y. \\
-c1y. \\
-c \when c2. \\
-c2.
-\end{gather} \\
-The sole answer set of $\p$ is
-$\lits = \set{a, b, c, c1x, c1y, c2}$.
-The only minimal proofs of literal $a$ wrt
-$\lits$ in $\p$ are
-the two sequences of rules $<5, 4, 3, 2, 1>$ and
-$<5, 4, 2, 3, 1>$.
-In both these proofs, the subproof of $c$ is $<5, 4, 3>$,
-which is nonminimal.
-(The minimal proof of $c$ wrt $\lits$ in $\p$ is $<7, 6>$.)
-
-\end{example}
-
-%:rule in P2
-\begin{lemma}
-\label{rule_in_P2}
-
-Let:
-\begin{enumerate}
-\item
-$\n\p1$ and $\n\p2$ be \hcf{} \ap{} programs with
-corresponding answer sets $\n\lits1 \setsp \n\lits2$
-\item
-$\lit \in \n\lits2 \setd \n\lits1$
-\end{enumerate}
-
-Then for each normal
-$\pr = \rlseq1n \in \prs\lit{\n\lits2}{\n\p2}$,
-there exists $\rl \in \pr$ such that
-$\rl \in \n\p2 \setd \n\p1$.
-
-\end{lemma}
-
-\begin{proof}
-
-Let $\rkn$ be the ranking function
-wrt $\n\lits2$ in $\n\p2$.
-We employ induction on $\rku\lit$.
-
-\begin{enumerate}
-
-\item
-Base step: $\rku\lit = min\set{\rku{\ot\lit} :
-\ot\lit \in \n\lits2 \setd \n\lits1}$.
-\begin{enumerate}
-\item
-To the contrary, assume for every $\rl \in \pr$, we have
-$\rl \in \n\p1 \seti \n\p2$.
-\item
-Then $\n\rl n \in \n\p1$.
-\item
-As $\pr$ is normal, for each
-$\ot\lit \in \posbody{\n\rl n}$,
-we have $\rku{\ot\lit} < \rku\lit$,
-so $\ot\lit \in \n\lits1$.
-\item
-Then $\n\rl n$ fires wrt $\n\lits1$.
-\item
-As $\n\lits1$ is an answer set of $\n\p1$, we know
-$\n\lits1$ satisfies $\head{\n\rl n}$.
-\item
-Let $\ot\lit \in \head{\n\rl n}$.
-\begin{enumerate}
-\item
-Case 1 of 2: $\ot\lit = \lit$.
-We already assumed $\lit \in \n\lits2 \setd \n\lits1$.
-\item
-Case 2 of 2: $\ot\lit \ne \lit$.
-We have $\ot\lit \not\in \n\lits2$,
-so $\ot\lit \not\in \n\lits1$.
-\end{enumerate}
-\item
-So $\n\lits1$ does not satisfy $\head{\n\rl n}$,
-contradiction.
-\end{enumerate}
-\item
-Induction step: $\rku\lit \le max\set{\rku{\ot\lit} :
-\ot\lit \in \n\lits2 \setd \n\lits1}$.
-\begin{enumerate}
-\item
-Induction hypothesis: for each
-$\ot\lit \in \n\lits2 \setd \n\lits1$,
-let normal $\ot\pr \in \prs{\ot\lit}{\n\lits2}{\n\p2}$,
-if $\rku{\ot\lit} < \rku\lit$,
-then there exists ${\rl} \in \ot\pr$
-such that ${\rl} \in \n\p2 \setd \n\p1$.
-\item
-To the contrary, assume for every $\rl \in \pr$, we have
-$\rl \in \n\p1 \seti \n\p2$.
-\begin{enumerate}
-\item
-Case 1 of 2: there exists $\ot\lit \in \posbody{\n\rl n}$
-where $\ot\lit \in \n\lits2 \setd \n\lits1$.
-\begin{enumerate}
-\item
-Choose some $1 \le m \le n$ where
-$h_{\n\lits2}(\n\rl m) = \ot\lit$.
-\item
-As $\pr$ is normal, $\ot\pr = \n\rl1, \ldots, \n\rl m$ is a
-normal proof of
-$\ot\lit$ wrt $\n\lits2$ in $\n\p2$.
-\item
-Notice $\rku{\ot\lit} < \rku\lit$.
-\item
-By the induction hypothesis, $\ot\pr$ contains some
-${\rl} \in \n\p2 \setd \n\p1$.
-\item
-So $\pr$ also contains ${\rl}$.
-\item
-By our assumption, $\rl \in \n\p1 \seti \n\p2$,
-contradiction.
-\end{enumerate}
-\item
-Case 2 of 2: for every $\ot\lit \in \posbody{\n\rl n}$,
-we have $\ot\lit \in \n\lits1$.
-\begin{enumerate}
-\item
-Then $\n\rl n$ fires wrt $\n\lits1$.
-\item
-By our assumption, $\n\rl n \in \n\p1$.
-\item
-As $\n\lits1$ is an answer set of $\n\p1$, we know
-$\n\lits1$ satisfies $\head{\n\rl n}$.
-\item
-But $\head{\n\rl n} \seti \n\lits1 = \sete$, contradiction.
-\end{enumerate}
-\end{enumerate}
-\end{enumerate}
-
-\end{enumerate}
-
-\end{proof}
-
-\begin{remark}
-
-Let $\pr = \n\rl1, \ldots, \n\rl n \in \prs\lit\lits\p$. If
-$\pr$ is minimal, then:
-\begin{enumerate}
-\item
-$\pr$ is normal
-\item
-$\lit$ depends on $h_\lits(\n\rl i)$ for all $i < n$
-\end{enumerate}
-
-\end{remark}
-
-%:last lemma
-\begin{lemma}
-\label{last_lemma}
-
-Let $\p$ be a nondisjunctive acyclic \cp{} program.
-If $\p$ has answer sets $\n\lits1 \setsp \n\lits2$,
-then there exist literals $\n\lit1$ and $\n\lit2$ in
-$\head\pcr$ such that
-$\n\lit1$ depends on $\n\lit2$.
-
-\end{lemma}
-
-\begin{proof}
-
-Notations:
-\begin{enumerate}
-\item
-By the contrapositive of Proposition \ref{same_abductive_support_heads},
-there exist abductive supports
-$\n\rls1$ and $\n\rls2$ of $\p$ where
-$\head{\n\rls1} \ne \head{\n\rls2}$.
-\item
-Let $\ot{\n\rls1} = \factify{\appl{\n\rls1}}$ and
-$\ot{\n\rls2} = \factify{\appl{\n\rls2}}$.
-\item
-Let $\n\p1 = \preg \setu \ot{\n\rls1}$ and
-$\n\p2 = \preg \setu \ot{\n\rls2}$.
-By Lemma \ref{factify_answer_set},
-$\n\lits1$ and $\n\lits2$ are respectively answer sets of
-$\n\p1$ and $\n\p2$.
-\end{enumerate}
-
-We follow these steps:
-\begin{enumerate}
-\item
-By Lemma \ref{diff_cr_literals},
-since $\p$ is nondisjunctive, we have
-$|\ot{\n\rls1}| = |\n\rls1|$ and
-$|\ot{\n\rls2}| = |\n\rls2|$.
-\item
-Notice $|\n\rls1| = |\n\rls2| > 0$.
-\item
-Then $|\ot{\n\rls1}| = |\ot{\n\rls2}| > 0$.
-\item
-Observe $|\head{\ot{\n\rls1}}| = |\ot{\n\rls1}|$ and
-$|\head{\ot{\n\rls2}}| = |\ot{\n\rls2}|$.
-\item
-Thus $|\head{\ot{\n\rls1}}| = |\head{\ot{\n\rls2}}| > 0$.
-\item
-Recall $\head{\ot{\n\rls1}} = \head{\n\rls1} \ne
-\head{\n\rls2} = \head{\ot{\n\rls2}}$.
-\item
-Then $\head{\ot{\n\rls1}} \setd \head{\ot{\n\rls2}} \ne
-\sete$.
-\item
-Select some $\n\lit1 \in \head{\ot{\n\rls1}} \setd
-\head{\ot{\n\rls2}}$.
-\item
-Let $\n\rl1$ be the fact $(\n\lit1.)$ in
-$\ot{\n\rls1} \setd\ot{\n\rls2}$.
-\item
-Since $\n\lits1$ is an answer set of $\n\p1$, we have
-$\n\lit1 \in \n\lits1$.
-\item
-Recall $\n\lits1 \setsp \n\lits2$.
-Then $\n\lit1 \in \n\lits2$.
-
-\item
-As $\n\lits2$ is an answer set of $\n\p2$, there exists
-$\rl\in \n\p2$ which
-supports $\n\lit1$ wrt $\n\lits2$.
-\begin{enumerate}
-\item
-Case 1 of 2: there exists $\lit \in \posbody{\rl}$ where
-$\lit \in \n\lits2 \setd \n\lits1$.
-\begin{enumerate}
-\item
-Let minimal $\pr \in \prs\lit{\n\lits2}{\n\p2}$.
-\item
-By Lemma \ref{rule_in_P2}, there exists $\n\rl2 \in \pr$
-where $\n\rl2 \in \n\p2 \setd \n\p1$.
-\item
-Then $\n\rl2 \in \ot{\n\rls2} \setd \ot{\n\rls1} \sets
-\appl\pcr$.
-\item
-Let $h_{\n\lits2}(\n\rl2) = {\n\lit2} \in \head\pcr$.
-\item
-As $\pr$ is minimal, $\lit$ depends on $\n\lit2$.
-\item
-Recall $\n\lit1$ depends on $\lit$ in $\rl$.
-\item
-By transitivity, $\n\lit1$ depends on $\n\lit2$.
-\end{enumerate}
-\item
-Case 2 of 2: $\posbody{\rl} \sets \n\lits1$.
-We show this case is impossible.
-\begin{enumerate}
-\item
-Subcase 1 of 2: $\rl \in \n\p1 \seti \n\p2$.
-\begin{enumerate}
-\item
-Notice $\rl$ supports $\n\lit1$ wrt $\n\lits1$.
-\item
-By Lemma \ref{sole_supporting_rule}, since $\p$ is acyclic,
-we have $\rl = \n\rl1$.
-\item
-However, $\rl \in \n\p2$ whereas
-$\n\rl1 \in \n\p1 \setd \n\p2$, contradiction.
-\end{enumerate}
-\item
-Subcase 2 of 2: $\rl \in \n\p2 \setd \n\p1$.
-\begin{enumerate}
-\item
-So $\rl \in \ot{\n\rls2} \setd \ot{\n\rls1}$.
-\item
-Then $\rl$ is the fact $(\n\lit1.)$,
-which is exactly $\n\rl1$.
-\item
-However, we selected $\n\rl1$ from
-$\ot{\n\rls1} \setd \ot{\n\rls2}$
-while $\rl \in \ot{\n\rls2}$, contradiction.
-\end{enumerate}
-\end{enumerate}
-\end{enumerate}
-\end{enumerate}
-
-\end{proof}
-
-%:hcf nondisjunctive
-\begin{remark}
-\label{hcf_nondisjunctive}
-
-If a \cp{} program $\p$ is acyclic,
-then there exists a nondisjunctive acyclic \cp{} program
-$\ot\p$ equivalent to $\p$
-\cite[page 73, Theorem 4.17]{hcfb}.
-
-\end{remark}
-
-%:last theorem
-\begin{theorem}
-[Antichain Property of CR-Independent Acyclic
-\cp{} Programs]
-\label{last_theorem}
-
-Let $\p$ be an acyclic \cp{} program.
-If $\p$ is cr-independent,
-then $\p$ has antichain property.
-
-\end{theorem}
-
-\begin{proof}
-
-By Remark \ref{hcf_nondisjunctive},
-there exists a nondisjunctive acyclic \cp{} $\ot\p$
-equivalent to $\p$.
-By the contrapositive of Lemma \ref{last_lemma},
-$\ot\p$ has antichain property.
-Therefore, $\p$ has antichain property too.
-
-\end{proof}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Conclusion}
-
-We have found a reasonably weak syntactic condition
-which guarantees that
-a \cp{} program has antichain property:
-the program being acyclic and cr-independent.
-The future goal is to further relax
-this sufficient condition to extend the class of
-\cp{} programs known to have
-this desired semantic property.
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\section{Acknowledgment}
-
-We sincerely appreciate the significant guidance of \mg.
-This paper includes his proofs of
-Theorem \ref{antichain_a_prolog} and
-Lemma \ref{answer_set_subprogram}.
-We also thank Evgenii Balai for the
-informative discussions.
+\end{conjecture}
 
@@
 
-\newpage
-
-\bibliography{bibl}
-
 \end{document}

### 2017-04-18 src/game.h
.7% lol

@@ -60,7 +60,7 @@ const Long COUT_PERIOD = pow(2, 15) - 1;
 const auto COUT_WIDTH = setw(12);
 const auto COUT_PRECISION = setprecision(1);
 
-const Long START_COUNT = 444366848; // log.txt
+const Long START_COUNT = 460521472; // log.txt
 
 ////////////////////////////////////////////////////////////
 

### 2017-04-19 src/game.h
40d left

@@ -60,7 +60,7 @@ const Long COUT_PERIOD = pow(2, 15) - 1;
 const auto COUT_WIDTH = setw(12);
 const auto COUT_PRECISION = setprecision(1);
 
-const Long START_COUNT = 460521472; // log.txt
+const Long START_COUNT = 471728128; // log.txt
 
 ////////////////////////////////////////////////////////////
 

### 2017-04-19 src/game.h
2mo left

@@ -60,7 +60,7 @@ const Long COUT_PERIOD = pow(2, 15) - 1;
 const auto COUT_WIDTH = setw(12);
 const auto COUT_PRECISION = setprecision(1);
 
-const Long START_COUNT = 471728128; // log.txt
+const Long START_COUNT = 489652224; // log.txt
 
 ////////////////////////////////////////////////////////////
 

### 2017-04-20 src/game.h
45d 6x6

@@ -60,7 +60,7 @@ const Long COUT_PERIOD = pow(2, 15) - 1;
 const auto COUT_WIDTH = setw(12);
 const auto COUT_PRECISION = setprecision(1);
 
-const Long START_COUNT = 489652224; // log.txt
+const Long START_COUNT = 504954880; // log.txt
 
 ////////////////////////////////////////////////////////////
 

### 2017-04-20 src/game.h
164h elapsed, 52d left

@@ -60,7 +60,7 @@ const Long COUT_PERIOD = pow(2, 15) - 1;
 const auto COUT_WIDTH = setw(12);
 const auto COUT_PRECISION = setprecision(1);
 
-const Long START_COUNT = 504954880; // log.txt
+const Long START_COUNT = 520978432; // log.txt
 
 ////////////////////////////////////////////////////////////
 

### 2017-04-21 src/game.h
would actually take 90d to complete

@@ -60,7 +60,7 @@ const Long COUT_PERIOD = pow(2, 15) - 1;
 const auto COUT_WIDTH = setw(12);
 const auto COUT_PRECISION = setprecision(1);
 
-const Long START_COUNT = 520978432; // log.txt
+const Long START_COUNT = 541130752; // log.txt
 
 ////////////////////////////////////////////////////////////
 

### 2017-04-23 src/game.h
1% in 10days

@@ -60,7 +60,7 @@ const Long COUT_PERIOD = pow(2, 15) - 1;
 const auto COUT_WIDTH = setw(12);
 const auto COUT_PRECISION = setprecision(1);
 
-const Long START_COUNT = 592248832; // log.txt
+const Long START_COUNT = 654082048; // log.txt
 
 ////////////////////////////////////////////////////////////
 

### 2017-04-24 src/game.h
900d left ;P

@@ -60,7 +60,7 @@ const Long COUT_PERIOD = pow(2, 15) - 1;
 const auto COUT_WIDTH = setw(12);
 const auto COUT_PRECISION = setprecision(1);
 
-const Long START_COUNT = 654082048; // log.txt
+const Long START_COUNT = 679247872; // log.txt
 
 ////////////////////////////////////////////////////////////
 

### 2017-04-24 src/game.h
1%

@@ -60,7 +60,7 @@ const Long COUT_PERIOD = pow(2, 15) - 1;
 const auto COUT_WIDTH = setw(12);
 const auto COUT_PRECISION = setprecision(1);
 
-const Long START_COUNT = 679247872; // log.txt
+const Long START_COUNT = 696877056; // log.txt
 
 ////////////////////////////////////////////////////////////
 

### 2017-04-25 src/game.cc
inspect

@@ -45,7 +45,8 @@ void Space::inspectPreImage() {
       fiberSize / PRE_SPACE_SIZE;
     cout << "Grid index" << COUT_WIDTH << gridIndex <<
       COUT_WIDTH << COUT_PRECISION << fixed <<
-      currentPercentage << "%\n";
+      currentPercentage << "%" <<
+      COUT_WIDTH << fiberSize << "\n";
   }
 }
 

### 2017-04-25 src/main.cc

@@ -7,9 +7,9 @@ int main(int argc, const char *argv[]) {
     Space space(atoi(argv[1]));
     setRULES();
 
-    // space.inspectPreImage();
+    space.inspectPreImage();
 
-    space.isEachGrid4tupleJoinable();
+    // space.isEachGrid4tupleJoinable();
 
     // space.isEachGrid3tupleJoinable();
 

### 2017-04-26 old/game.py
style

@@ -66,7 +66,9 @@ class Game:
         image = set()
         superself = Game(self.grid_edge + 2)
         for supergrid in superself.get_domain():
-            next_supergrid = superself.get_next_grid(supergrid)
+            next_supergrid = superself.get_next_grid(
+                supergrid
+            )
             next_grid = superself.get_subgrid(next_supergrid)
             image.add(next_grid)
         return image
@@ -84,7 +86,7 @@ class Game:
         image = set()
         for grid in self.get_domain():
             next_grid = self.get_next_grid(grid)
-            image.add(self.get_next_grid(grid))
+            image.add(next_grid)
         return image
 
     def get_domain_size(self) -> int:
@@ -126,7 +128,9 @@ class Game:
                 self.lower_birth, self.upper_birth
             )
 
-    def get_cell_state(self, grid: Grid, cell: Cell) -> CellState:
+    def get_cell_state(
+        self, grid: Grid, cell: Cell
+    ) -> CellState:
         for ind in cell:
             if ind < 0 or ind >= self.grid_edge:
                 return False
@@ -136,7 +140,10 @@ class Game:
         D = {-1, 0, 1}
         row_inds = {cell[0] + d for d in D}
         col_inds = {cell[1] + d for d in D}
-        cells = {(row, col) for row in row_inds for col in col_inds}
+        cells = {
+            (row, col)
+            for row in row_inds for col in col_inds
+        }
         cells.remove(cell)
         return cells
 

### 2017-04-26 old/main.py

@@ -10,19 +10,29 @@ GRID_EDGE_MAX_PROP = 3 # auto +2 if superly; 5 crashes Vu-PC
 
 def get_speedup_str() -> str:
     sts = [get_aligned_str('grid edge', 'speedup')]
-    for grid_edge in range(game.GRID_EDGE_MIN, GRID_EDGE_MAX_SPEEDUP + 1):
+    for grid_edge in range(
+        game.GRID_EDGE_MIN, GRID_EDGE_MAX_SPEEDUP + 1
+    ):
         speedup = trapdoor.get_trapdoor_speedup(grid_edge)
         sts.append(get_aligned_str(grid_edge, speedup))
     return '\n'.join(sts)
 
 def get_prop_str() -> str:
-    sts = [get_aligned_str('grid edge', 'proportion', 'time (secs)')]
-    for grid_edge in range(game.GRID_EDGE_MIN, GRID_EDGE_MAX_PROP + 1):
+    sts = [
+        get_aligned_str(
+            'grid edge', 'proportion', 'time (secs)'
+        )
+    ]
+    for grid_edge in range(
+        game.GRID_EDGE_MIN, GRID_EDGE_MAX_PROP + 1
+    ):
         time_start = time.time()
         g = game.Game(grid_edge)
         prop = g.get_image_prop(superly=True)
         time_taken = time.time() - time_start
-        sts.append(get_aligned_str(grid_edge, prop, time_taken))
+        sts.append(
+            get_aligned_str(grid_edge, prop, time_taken)
+        )
     return '\n'.join(sts)
 
 def get_aligned_str(*args) -> str:

### 2017-04-27 old/game.py
style

@@ -69,7 +69,9 @@ class Game:
             next_supergrid = superself.get_next_grid(
                 supergrid
             )
-            next_grid = superself.get_subgrid(next_supergrid)
+            next_grid = superself.get_subgrid(
+                next_supergrid
+            )
             image.add(next_grid)
         return image
 

### 2017-04-27 old/main.py

@@ -6,7 +6,7 @@ import game
 import trapdoor
 
 GRID_EDGE_MAX_SPEEDUP = 200
-GRID_EDGE_MAX_PROP = 3 # auto +2 if superly; 5 crashes Vu-PC
+GRID_EDGE_MAX_PROP = 2 # auto +2 if superly; 5 crashes Vu-PC
 
 def get_speedup_str() -> str:
     sts = [get_aligned_str('grid edge', 'speedup')]

### 2017-04-27 old/trapdoor.py

@@ -10,7 +10,9 @@ def get_trapdoor_speedup(grid_edge: int) -> float:
 
 def get_time_no_trapdoor(grid_edge: int) -> int:
     time = 0
-    for poss_grid_edge in range(game.GRID_EDGE_MIN, grid_edge + 1):
+    for poss_grid_edge in range(
+        game.GRID_EDGE_MIN, grid_edge + 1
+    ):
         time +=get_time_trapdoor(poss_grid_edge)
     return time
 

### 2017-05-15 monico/gol5x5.c
Dr. Monico

@@ -1,3 +1,5 @@
+/* author: Dr. Monico */
+
 #include <stdio.h>
 #include <string.h>
 #include <stdlib.h>

### 2017-05-15 paper/paper.tex
conjecture
for each
notations
C(n)
60char
sizes
rearranged sections
life poly
20pt
Dr. Monico checked 5x5 in 5 days
proportion
style

@@
-\documentclass{paper}
+\documentclass[letterpaper, 14pt]{extarticle}
+% 8pt, 9pt, 10pt, 11pt, 12pt, 14pt, 17pt, 20pt
+
+\usepackage[scale=0.9]{geometry}
+
+\usepackage{paper}
 
@@
 \begin{center}
-{\Large \mytitle}
+\Large{\mytitle}
 \end{center}
-
-\bigskip
-
-\begin{abstract}
-Game of Life.
-\end{abstract}
-
-\bigskip
 
@@
 
-\section{Notations}
+\section{Counting}
 
-For each $n \in \Zplus$:
-\begin{enumerate}
-\item let $\sp{n} = \Ftwo ^ {\Zn ^ 2}$
-\item let $\l: \sp{n+2} \to \sp{n}$
-\end{enumerate}
+\begin{remark}
+Case counts (precell state $\to$ cell state):
+\begin{itemize}
+\item $0 \to 1$ $$\binom{8}{3}$$
+\item $0 \to 0$ $$2^8 - \binom{8}{3}$$
+\item $1 \to 1$ $$\binom{8}{2} + \binom{8}{3}$$
+\item $1 \to 0$ $$2^8 - \binom{8}{2} - \binom{8}{3}$$
+\end{itemize}
+\end{remark}
 
@@
 
-\section{Results}
+\section{Functions}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Cell Function}
+
+\begin{definition}
+Polynomial function:
+\begin{itemize}
+\item Let cell $\cell \in \Ft$ and
+  neighbors $\neighbors \in \Ft$.
+\item Let polynomial $\lp \in \pr$.
+\item Let \textdef{cell function}
+  $\pf: \Ft \times \Fte \to \Ft$.
+\end{itemize}
+\end{definition}
+
+\begin{remark}
+Explicit form:
+\begin{dmath*}
+\lp = (\cell + 1) *
+\sum_{i \ne j \ne k, k \ne i}\parentheses
+{\cell_i \cell_j \cell_k
+\prod_{m \ne i, j, k}(\cell_m + 1)} + \\
+\cell * \parentheses
+{\sum_{i \ne j}\parentheses
+{\cell_i \cell_j \prod_{m \ne i, j}(\cell_m + 1)} + \\
+\sum_{i \ne j \ne k, k \ne i}\parentheses
+{\cell_i \cell_j \cell_k
+\prod_{m \ne i, j, k}(\cell_m + 1)}}
+\end{dmath*}
+\end{remark}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsection{Grid Function}
+
+\begin{definition}
+For each $n \in \Zplus$:
+\begin{itemize}
+\item Let set $\sp{n} = \FtZns =
+  \set{grid: \Zn \times \Zn \to \Ft}$.
+\item Let \textdef{grid function} $\lf{n}: \sp{n+2} \to \sp{n}$.
+\end{itemize}
+\end{definition}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsubsection{Cardinalities}
+
+\begin{remark}
+Cardinalities related to $\lf{n}$:
+\begin{itemize}
+\item domain: $D_n = 2^{(n+2)^2}$
+\item codomain: $C_n = 2^{n^2}$
+\item image: $I_n \le C_n$
+\item proportion: $P_n = I_n / C_n \le 1$
+\item average fiber: $D_n / I_n \ge D_n / C_n = 2^{4(n+1)}$
+\end{itemize}
+\end{remark}
+
+\begin{remark}[joining small grids into a big grid]
+Let $k \in \Zplus$. Then:
+$$P_{k n} = \frac{I_{k n}}{C_{k n}}
+= \frac{I_{k n}}{(C_n)^{k^2}}
+\le \frac{{(I_n)}^{k^2}}{(C_n)^{k^2}}
+= \parentheses{\frac{I_n}{C_n}}^{k^2}
+= (P_n)^{k^2}$$
+If $P_n < 1$ for some $n$,
+then $\lim_{k \to \infty} P_{kn} = 0$.
+\end{remark}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\subsubsection{Surjectivity}
+
+\begin{definition}
+Let proposition $\cs{n}$ be: $\lf{n}$ is surjective.
+\end{definition}
+
+\begin{remark}
+For each $n \in \set{1, 2, 3, 4}$, $\cs{n}$ is true.
+\end{remark}
+
+\begin{remark}
+\cm's code: $\cs5$ is true (5-day runtime).
+\end{remark}
+
+\begin{remark}
+Vu's code: $\cs6$ is \emph{likely} true \\
+(1\% complete, 10 days elapsed, 3 years left).
+\end{remark}
 
 \begin{conjecture}
-
+For each $n \in \Zplus$, $\cs{n}$ is true.
 \end{conjecture}

### 2017-05-18 paper/paper.tex
style
possibly

@@
   \set{grid: \Zn \times \Zn \to \Ft}$.
-\item Let \textdef{grid function} $\lf{n}: \sp{n+2} \to \sp{n}$.
+\item Let \textdef{grid function}
+  $\lf{n}: \sp{n+2} \to \sp{n}$.
 \end{itemize}
@@
 \begin{definition}
-Let proposition $\cs{n}$ be: $\lf{n}$ is surjective.
+Let proposition $\cs{n}$ be ``$\lf{n}$ is surjective''.
 \end{definition}
@@
 \begin{remark}
-Vu's code: $\cs6$ is \emph{likely} true \\
+Vu's code: $\cs6$ is \emph{possibly} true \\
 (1\% complete, 10 days elapsed, 3 years left).
